### 2012-11-05 proposal/paper.tex
Initial Proposal

% Term paper proposal.

\documentclass[]{IEEEtran}

\usepackage{float}
\usepackage{url}
\usepackage{graphicx}
\usepackage{color}

\begin{document}

\title{AutoCiter: Let's Go Cite-Seeing!}

% author names and affiliations
% use a multiple column layout for up to two different
% affiliations

\author{\IEEEauthorblockN{Eriq Augustine, Aldrin Montana, Ryan Verdon}
\\
\IEEEauthorblockA{Department of Computer Science\\
Cal Poly, San Luis Obispo\\
 \textsf{eaugusti@calpoly.edu, amontant@calpoly.edu, rverdon@calpoly.edu}
}
}

\maketitle

\thispagestyle{empty}
\pagestyle{empty}

\section{Introduction}
We will be doing the Auto-Citer project. We LOVE acedemic papers.

\section{Problem Description}
The probem of auto-citation can be broken up into two cases.

\subsection{Known Location}
In this case, the location of the citation is known, but the proper paper index is unknown.

\subsection{Unknown Location}
In this case, the list of citations is known. However, there is no citation markers in the paper.

\section{Background}
Taken alone, this problem does not solve many questions in the wild. However without loss of generality, these
methods should be able to be used on a larger scale to make citation reccomendations.

\section{Dataset}
We will be acquiring our dataset from the ACM Digital Library. The dataset will include multiple
papers where most of the references are also available on the ACM DL. Both the main paper and the
references will be included in out final dataset.

On the ACM DL, only read-only (usually PDF) versions of the papers are supplied.
To make things easier, we will be pre-prossing the PDFs and converting them into plain text files.

\subsection{Test Dataset}
For our testing dataset, we will remove the citation index from the citation markers. For example,
``[164]'' will become ``[]''. If there are multiple cites in the same sentence, then we will break this up into
many single citations. ``[1, 2, 3]'' or ``[1][2][3]'' will become ``[][][]''. However if we do not have access to the
text of one of the citations, then we will just leave that citation marker. So if citation 2 is not available,
``[1, 2]'' will become ``[][2]''.

For the problem where we do not know where the citation marker belongs, then will just remove all markers from the paper.

\section{Proposed Methods}
We have yet to decide what language we will be using for this project, but we will probably either use the WEKA machine learning
packageweka\cite{weka} or NLTK\cite{nltk}.

\bibliographystyle{acm}
\bibliography{refs}

\end{document}

### 2012-12-01 code/citer/citer.py
Moving around some code

@@ -1,8 +1,13 @@
 import method
 import parser
+import sys
 
 def main():
-   paper = parser.parseFullDataset('data/dynamo')
+   #paper = parser.parseFullDataset('data/dynamo')
+   paperName = 'data/Comparative Analysis of RNA Families Reveals Distinct Repertoires for Each Domain of Life'
+   if len(sys.argv) > 1:
+      paperName = sys.argv[1]
+   paper = parser.parseFullDataset(paperName)
    print paper
 
    debugRun(paper)
@@ -17,6 +22,11 @@ def debugRun(paper):
    for i in range(0, len(paper.citations)):
       cite = paper.citations[i]
       correctReference = paper.citationKey[i]
+
+      # Skip citations that do not have a reference.
+      if not paper.references.has_key(correctReference):
+         print "Warning: There is no citation information found for citation #{}, skipping".format(correctReference)
+         next
 
       print '---------'
       print cite.paragraphContext.raw

### 2012-12-01 code/citer/citer.py
Refactored some of the method flow and included dates in pronouns

@@ -4,7 +4,7 @@ import sys
 
 def main():
    #paper = parser.parseFullDataset('data/dynamo')
-   paperName = 'data/Comparative Analysis of RNA Families Reveals Distinct Repertoires for Each Domain of Life'
+   paperName = '../data/A Bayesian Inference Framework to Reconstruct Transmission Trees Using Epidemiological and Genetic Data'
    if len(sys.argv) > 1:
       paperName = sys.argv[1]
    paper = parser.parseFullDataset(paperName)
@@ -14,10 +14,14 @@ def main():
 
 def debugRun(paper):
    methods = []
-   methods.append(method.ProperNounMethod(paper))
-   methods.append(method.AbstractMethod(paper))
+   methods.append(method.TitleAuthorMethod(paper))
+   methods.append(method.SentenceContextAbstractBigramsMethod(paper))
+   methods.append(method.SentenceContextAbstractWordsMethod(paper))
+   methods.append(method.ParagraphContextAbstractBigramsMethod(paper))
+   methods.append(method.ParagraphContextAbstractWordsMethod(paper))
 
    hits = 0
+   misses = 0
 
    for i in range(0, len(paper.citations)):
       cite = paper.citations[i]
@@ -43,11 +47,15 @@ def debugRun(paper):
             reportedValue = True
             if guess == correctReference:
                hits += 1
+            else:
+               misses += 1
+
       print res
       print "Actual Reference: {0}".format(correctReference)
       print '---------'
 
-   print "{0} / {1} ({2})".format(hits, len(paper.citations), hits / float(len(paper.citations)))
+   print "HITS: {0} / {1} ({2})".format(hits, len(paper.citations), hits / float(len(paper.citations)))
+   print "Misses: {0}".format(misses)
 
 if __name__ == "__main__":
    main()

### 2012-12-01 code/citer/method.py

@@ -9,13 +9,64 @@ import util
 # WARNING: A Method may maintain state data about the citations it has done.
 #  This is very important in the cases that there are multiple cites in a single context (sentence, paragraph, etc).
 #  Therefore, you should only use a method instance on one citation cycle (itteration through the paper).
-class Method:
+class Method(object):
    # Return None if you can't make a guess.
-   def guess(cite, paper):
+   def guess(self, cite, paper):
       return None
 
-class ProperNounMethod(Method):
+class ContextMethod(Method):
+   def __init__(self):
+      # There will be no more than one citation per reference per context (probably).
+      self.contextHistory = {}
+
+   # Get the context that the current Method uses from the reference.
+   # This is assumed to be a map of {refKey: [ context grams ]}.
+   def getReferenceContext(self, paper):
+      print "WARNING: Base getReferenceContext() called."
+      return None
+
+   # Get the context that the current Method uses from the cite.
+   def getCiteContext(self, cite):
+      print "WARNING: Base getCiteContext() called."
+      return None
+
+   # Split the context
+   def getCiteContextGrams(self, cite):
+      print "WARNING: Base getCiteContext() called."
+      return None
+
+   def guess(self, cite, paper):
+      context = self.getCiteContext(cite)
+      grams = self.getCiteContextGrams(cite)
+
+      # Get the citation history for this context
+      if not self.contextHistory.has_key(context):
+         self.contextHistory[context] = set()
+      history = self.contextHistory[context]
+
+      maxIntersection = 0
+      bestRef = None
+
+      #TEST
+      print grams
+
+      for (referenceKey, abstractGrams) in self.getReferenceContext(paper).items():
+         if not referenceKey in history:
+            intersection = len(abstractGrams & grams)
+            if intersection > maxIntersection:
+               maxIntersection = intersection
+               bestRef = referenceKey
+
+      if bestRef:
+         history.add(bestRef)
+         return int(bestRef)
+
+      return None
+
+class TitleAuthorMethod(ContextMethod):
    def __init__(self, paper):
+      super(TitleAuthorMethod, self).__init__()
+
       # Pre-build a list of all proper nouns in the references' title and authors.
       self.properNouns = {}
 
[…]

### 2012-12-01 code/citer/paper.py

@@ -1,5 +1,7 @@
 import re
 
+import util
+
 class Paper:
    # |parseStructire| is assumed to be a dict generated from parser::parseFullDataset().
    def __init__(self, parseStructure, root = True):
@@ -28,6 +30,20 @@ class Paper:
          self.noNumbersText = parseStructure['root']['noNumbersText']
          self.citationKey = parseStructure['root']['citationKey']
          self.citations = parseStructure['root']['citations']
+
+         # Do pre-processing on the citations.
+         for citation in self.citations:
+            # proper nouns
+            citation.sentenceProperNouns = util.removeStopwords(util.getCapitalWords(citation.sentenceContext.noCitations))
+            citation.paragraphProperNouns = util.removeStopwords(util.getCapitalWords(citation.paragraphContext.noCitations))
+
+            # bigrams
+            citation.sentenceBigrams = util.getNonStopNgrams(citation.sentenceContext.noCitations, 2)
+            citation.paragraphBigrams = util.getNonStopNgrams(citation.paragraphContext.noCitations, 2)
+
+            # Add important unigrams to the proper nouns
+            citation.sentenceProperNouns.update(util.importantUnigrams(citation.sentenceBigrams))
+            citation.paragraphProperNouns.update(util.importantUnigrams(citation.paragraphBigrams))
 
          # This is a dict to accomodate missing references, and index by 1.
          self.references = {}

### 2012-12-01 code/citer/util.py

@@ -12,6 +12,24 @@ STEMMER = StupidStemmer()
 # Note: It convention for this code base to represent a unigram (and therefore
 # n-grams) as all capital.
 
+# Given some bigrams, find the unigrams that occur >= 25% of the time.
+def importantUnigrams(bigrams):
+   unigrams = set()
+
+   counts = {}
+   for bigram in bigrams:
+      for word in bigram.split('-'):
+         word = STEMMER.stem(word)
+         if not counts.has_key(word):
+            counts[word] = 1
+         else:
+            counts[word] += 1
+   for (word, count) in counts.items():
+      if float(count) / len(bigrams) >= 0.25:
+         unigrams.add(word)
+
+   return unigrams
+
 # Given a dict of sets, return a new dict of matching sets where each item
 # is unique to that set.
 # n is the number of sets that a word is allowed to belong in.
@@ -51,8 +69,9 @@ def uniqueSets(sets, n = 1):
 
 # TODO(eriq): Watch the first capital.
 # This really aims to get proper nouns.
+# Numbers count!
 def getCapitalWords(text):
-   words = re.findall('(?<![a-z])[A-Z]\w+', text)
+   words = re.findall('(?<![a-z])(?:(?:[A-Z]\w+)|\d+)', text)
    return set([word.upper() for word in words])
 
 # This will split the text into a list (NOT SET) of unigrams.

### 2012-12-01 code/citer/citer.py
Added PreContext

@@ -1,24 +1,69 @@
+import sys
+import operator
+
+from constants import DEBUG
+
 import method
 import parser
-import sys
+
+AVAILABLE_METHODS = [
+                     method.PreContextTitleAuthorMethod,
+                     method.SentenceTitleAuthorMethod,
+                     method.SentenceContextAbstractBigramsMethod,
+                     method.ParagraphContextAbstractBigramsMethod,
+                     method.SentenceContextAbstractWordsMethod,
+                     method.ParagraphContextAbstractWordsMethod,
+                    ]
 
 def main():
    #paper = parser.parseFullDataset('data/dynamo')
    paperName = '../data/A Bayesian Inference Framework to Reconstruct Transmission Trees Using Epidemiological and Genetic Data'
-   if len(sys.argv) > 1:
-      paperName = sys.argv[1]
+   #if len(sys.argv) > 1:
+   #   paperName = sys.argv[1]
    paper = parser.parseFullDataset(paperName)
    print paper
 
-   debugRun(paper)
+   # Ordering mode
+   if '-o' in sys.argv:
+      orderingRun(paper)
+   else:
+      debugRun(paper)
+
+# This one runs all the mothods in isolation and then tries to give a suggested ordering.
+# Highest precision first.
+def orderingRun(paper):
+   methods = [ method(paper) for method in AVAILABLE_METHODS ]
+   res = {}
+
+   for methodObj in methods:
+      hits = 0
+      misses = 0
+
+      for i in range(0, len(paper.citations)):
+         cite = paper.citations[i]
+         correctReference = paper.citationKey[i]
+
+         # Skip citations that do not have a reference.
+         if not paper.references.has_key(correctReference):
+            next
+
+         guess = methodObj.guess(cite, paper)
+         if guess == correctReference:
+            hits += 1
+         elif guess:
+            misses += 1
+
+      print "{} -- Misses: {}".format(methodObj.__class__.__name__, misses)
+      res[methodObj.__class__.__name__] = misses
+
+   print ''
+   res = sorted(res.iteritems(), key=operator.itemgetter(1))
+   for (methodName, misses) in res:
+      print methodName
+
 
 def debugRun(paper):
-   methods = []
-   methods.append(method.TitleAuthorMethod(paper))
-   methods.append(method.SentenceContextAbstractBigramsMethod(paper))
-   methods.append(method.SentenceContextAbstractWordsMethod(paper))
[…]

### 2012-12-01 code/citer/constants.py

@@ -1,0 +1,3 @@
+import sys
+
+DEBUG = '-d' in sys.argv

### 2012-12-01 code/citer/method.py

@@ -1,6 +1,7 @@
 import re
 
 import util
+from constants import DEBUG
 
 # The general class for algorithms that try and solve for citations.
 # The hope is that every algorithm extends Method in the same pattern
@@ -26,6 +27,7 @@ class ContextMethod(Method):
       return None
 
    # Get the context that the current Method uses from the cite.
+   # This is mainly used to resolve history issues.
    def getCiteContext(self, cite):
       print "WARNING: Base getCiteContext() called."
       return None
@@ -47,8 +49,8 @@ class ContextMethod(Method):
       maxIntersection = 0
       bestRef = None
 
-      #TEST
-      print grams
+      if DEBUG:
+         print grams
 
       for (referenceKey, abstractGrams) in self.getReferenceContext(paper).items():
          if not referenceKey in history:
@@ -63,35 +65,58 @@ class ContextMethod(Method):
 
       return None
 
-class TitleAuthorMethod(ContextMethod):
+# Title/Author methods
+
+class BaseTitleAuthorMethod(ContextMethod):
+   properNouns = None
+
    def __init__(self, paper):
-      super(TitleAuthorMethod, self).__init__()
+      super(BaseTitleAuthorMethod, self).__init__()
+
+      if BaseTitleAuthorMethod.properNouns:
+         return
 
       # Pre-build a list of all proper nouns in the references' title and authors.
-      self.properNouns = {}
+      BaseTitleAuthorMethod.properNouns = {}
 
       # TODO(eriq): remove stopwords and try to remove other capitilization false positives.
       for (key, reference) in paper.references.items():
-         # Make sure to avoid initials.
-         authorNouns = re.findall('\w{2,}', ' '.join(reference.authors))
-         self.properNouns[key] = set([authorNoun.upper() for authorNoun in authorNouns])
-         self.properNouns[key] |= util.removeTitleStopwords(util.getCapitalWords(reference.title))
+         # Make sure to avoid initials (and double initials).
+         authorNouns = re.findall('\w{3,}', ' '.join(reference.authors))
+         BaseTitleAuthorMethod.properNouns[key] = set([authorNoun.upper() for authorNoun in authorNouns])
[…]

### 2012-12-01 code/citer/paper.py

@@ -1,6 +1,7 @@
 import re
 
 import util
+import parser
 
 class Paper:
    # |parseStructire| is assumed to be a dict generated from parser::parseFullDataset().
@@ -82,3 +83,17 @@ class Citation:
                                      markedSentence, citesPerSentence)
       self.paragraphContext = Context(paragraph, noCitesParagraph, noNumbersParagraph,
                                      markedParagraph, citesPerParagraph)
+
+      # Figure out the pre context
+      self.preContext = ''
+      # Check for a para surround first.
+      match = re.search('\(([^\)]*{}[^\(]*)\)'.format(re.escape(parser.MARKED_CITATION_MARKER)), markedSentence)
+      if match:
+         self.preContext = match.group(1).replace(parser.MARKED_CITATION_MARKER, ' ').strip()
+      else:
+         match = re.search('([^\[\]\.,;:!"\-]+){}'.format(re.escape(parser.MARKED_CITATION_MARKER)), markedSentence)
+
+         if match:
+            self.preContext = match.group(1).strip()
+
+      self.preContextUnigrams = util.getNonStopNgrams(self.preContext, 1)

### 2012-12-01 code/citer/util.py

@@ -12,6 +12,31 @@ STEMMER = StupidStemmer()
 # Note: It convention for this code base to represent a unigram (and therefore
 # n-grams) as all capital.
 
+# Normalize some formatting
+def normalize(text):
+   modText = text
+
+   # c2 a0 = nbsp
+   modText = re.sub('\xc2\xa0', '', modText)
+   # e2 80 9c = left double quote
+   modText = re.sub('\xe2\x80\x9c', '"', modText)
+   # e2 80 9d = right double quote
+   modText = re.sub('\xe2\x80\x9d', '"', modText)
+   # e2 80 99 = right single quote
+   modText = re.sub('\xe2\x80\x99', '\'', modText)
+   # c3 a9 = e with accent aigu
+   modText = re.sub('\xc3\xa9', 'e', modText)
+   # c3 a9 = e with accent grave
+   modText = re.sub('\xc3\xa8', 'e', modText)
+   # e2 80 93 = EN dash
+   modText = re.sub('\xe2\x80\x93', '-', modText)
+   # c3 ab e with umlat
+   modText = re.sub('\xc3\xab', 'e', modText)
+   # c5 93 (oe guy)
+   modText = re.sub('\xc5\x93', 'oe', modText)
+
+   return modText
+
 # Given some bigrams, find the unigrams that occur >= 25% of the time.
 def importantUnigrams(bigrams):
    unigrams = set()

### 2012-12-02 code/citer/citer.py
Added a main that goes through all the different datasets.

@@ -1,5 +1,6 @@
-import sys
 import operator
+import os
+import sys
 
 from constants import DEBUG
 
@@ -16,8 +17,14 @@ AVAILABLE_METHODS = [
                     ]
 
 def main():
+   # full test mode
+   if '-f' in sys.argv:
+      fullTest()
+      return
+
    #paper = parser.parseFullDataset('data/dynamo')
-   paperName = '../data/A Bayesian Inference Framework to Reconstruct Transmission Trees Using Epidemiological and Genetic Data'
+   #paperName = '../data/A Bayesian Inference Framework to Reconstruct Transmission Trees Using Epidemiological and Genetic Data'
+   paperName = '../data/A Graphical Modelling Approach to the Dissection of Highly Correlated Transcription Factor Binding Site Profiles'
    #if len(sys.argv) > 1:
    #   paperName = sys.argv[1]
    paper = parser.parseFullDataset(paperName)
@@ -28,6 +35,57 @@ def main():
       orderingRun(paper)
    else:
       debugRun(paper)
+
+def fullTest():
+   res = []
+   for paperName in os.listdir('../data'):
+      paper = None
+
+      try:
+         paper = parser.parseFullDataset('../data/' + paperName)
+         res.append(normalRun(paper))
+      except OSError:
+         print "Error parsing paper: " + paperName
+         next
+
+   res = sorted(res, reverse = True)
+   for paper in res:
+      print paper[1]
+
+def normalRun(paper):
+   methods = [ method(paper) for method in AVAILABLE_METHODS ]
+
+   hits = 0
+   misses = 0
+   # Don't count references without any information
+   total = 0
+
+   for i in range(0, len(paper.citations)):
+      cite = paper.citations[i]
+      correctReference = paper.citationKey[i]
+
+      # Skip citations that do not have a reference.
+      if not paper.references.has_key(correctReference):
+         next
+
+      total += 1
+
+      # Don't count if a value is unreported (earlier phases of the pipeline do not report).
+      # But make sure to only count a hit once.
+      reportedValue = False
+      for methodObj in methods:
+         guess = methodObj.guess(cite, paper)
+         if guess:
+            if guess == correctReference:
+               hits += 1
+            else:
+               misses += 1
+            break
+
+   #print "{} (Hits: {}, Misses: {}, Total: {}) -- {}".format((float(hits) / total), hits, misses, total, paper.title)
[…]

### 2012-12-02 code/citer/method.py

@@ -68,33 +68,35 @@ class ContextMethod(Method):
 # Title/Author methods
 
 class BaseTitleAuthorMethod(ContextMethod):
-   properNouns = None
+   properNouns = {}
 
    def __init__(self, paper):
       super(BaseTitleAuthorMethod, self).__init__()
 
-      if BaseTitleAuthorMethod.properNouns:
+      if BaseTitleAuthorMethod.properNouns.has_key(paper.title):
          return
 
       # Pre-build a list of all proper nouns in the references' title and authors.
-      BaseTitleAuthorMethod.properNouns = {}
+      paperProperNouns = {}
 
       # TODO(eriq): remove stopwords and try to remove other capitilization false positives.
       for (key, reference) in paper.references.items():
          # Make sure to avoid initials (and double initials).
          authorNouns = re.findall('\w{3,}', ' '.join(reference.authors))
-         BaseTitleAuthorMethod.properNouns[key] = set([authorNoun.upper() for authorNoun in authorNouns])
-         BaseTitleAuthorMethod.properNouns[key] |= util.removeTitleStopwords(util.getCapitalWords(reference.title))
+         paperProperNouns[key] = set([authorNoun.upper() for authorNoun in authorNouns])
+         paperProperNouns[key] |= util.removeTitleStopwords(util.getCapitalWords(reference.title))
 
-      BaseTitleAuthorMethod.properNouns = util.uniqueSets(BaseTitleAuthorMethod.properNouns, 1)
+      paperProperNouns = util.uniqueSets(paperProperNouns, 1)
 
       if DEBUG:
          print "Title/Author:"
-         for (ref, nouns) in BaseTitleAuthorMethod.properNouns.items():
+         for (ref, nouns) in paperProperNouns.items():
             print "{0} -- {1}".format(ref, nouns)
 
+      BaseTitleAuthorMethod.properNouns[paper.title] = paperProperNouns
+
    def getReferenceContext(self, paper):
-      return BaseTitleAuthorMethod.properNouns
+      return BaseTitleAuthorMethod.properNouns[paper.title]
 
 class SentenceTitleAuthorMethod(BaseTitleAuthorMethod):
    def __init__(self, paper):
@@ -119,28 +121,28 @@ class PreContextTitleAuthorMethod(BaseTitleAuthorMethod):
 # ABSTRACT methods
 
 class BaseAbstractMethod(ContextMethod):
-   abstractWords = None
[…]

### 2012-12-02 code/citer/citer.py
Working on citer driver

@@ -25,8 +25,8 @@ def main():
    #paper = parser.parseFullDataset('data/dynamo')
    #paperName = '../data/A Bayesian Inference Framework to Reconstruct Transmission Trees Using Epidemiological and Genetic Data'
    paperName = '../data/A Graphical Modelling Approach to the Dissection of Highly Correlated Transcription Factor Binding Site Profiles'
-   #if len(sys.argv) > 1:
-   #   paperName = sys.argv[1]
+   if '-p' in sys.argv:
+      paperName = sys.argv[sys.argv.index('-p') + 1]
    paper = parser.parseFullDataset(paperName)
    print paper
 

### 2012-12-02 code/plos_scraper/directory_fixer_upper.pl
Added perl script to fix incorrect reference directory structures
fixed scraper script to correctly write reference directory structures, plus
fixed the search page scraping. It was previously scraping a search page
multiple times due to changing javascript session IDs

@@ -1,0 +1,112 @@
+#!/usr/bin/perl
+use strict;
+use warnings;
+
+use Carp;
+use Cwd;
+use File::Copy;
+
+use constant ROOT_DIR => getcwd().'/data/';
+
+sub dir_status {
+   if ($ENV{DEBUG}) {
+      print("current directory: ".getcwd()."\n");
+   }
+}
+
+sub read_dir {
+   my ($dir_handle) = @_;
+
+   return grep { $_ !~ m/[.]+/ } readdir($dir_handle);
+}
+
+sub dir_map {
+   my ($success, $dir_name, $anon_func) = (0, @_);
+
+   if (-d $dir_name && chdir($dir_name)) {
+      dir_status();
+      &$anon_func();
+      $success = 1;
+      chdir(q{..});
+      dir_status();
+   }
+
+   return $success;
+}
+
+sub hoist_references {
+   opendir(my $REF_DIR, getcwd()) or croak('Unable to open current directory');
+
+   my $DIR_BEGIN = telldir($REF_DIR);
+
+   # A loop to pull all sub directories up to current directory
+   for my $sub_dir (read_dir($REF_DIR)) {
+      dir_map($sub_dir, sub {
+         hoist_references();
+      });
+   }
+   closedir($REF_DIR);
+
+   opendir($REF_DIR, getcwd()) or croak('Unable to open current directory');
+
+   for my $sub_dir (read_dir($REF_DIR)) {
+      if (-d $sub_dir) {
+         my ($abs_sub_dir, $parent_dir) = (getcwd()."/$sub_dir", getcwd().'/..');
+         print("move '$abs_sub_dir' '$parent_dir\n'");
+
+         if (!$ENV{DEBUG}) {
+            #move($abs_sub_dir, $parent_dir) or croak("error moving file: $!");
+            `mv "$abs_sub_dir" "$parent_dir"`;
+            #print `pwd`;
+            #print `ls`;
+         }
+      }
+   }
+
+   closedir($REF_DIR);
+
+}
+
+sub fix_ref_dir {
+   my ($paper_dir) = @_;
+
+   my $success = dir_map("$paper_dir/references", sub {
+      opendir(my $REF_DIR, getcwd()) or croak('Unable to open cwd');
+
+      for my $sub_dir (read_dir($REF_DIR)) {
+         dir_map($sub_dir, sub {
+            hoist_references();
+         });
+      }
+      closedir($REF_DIR);
+
[…]

### 2012-12-02 code/plos_scraper/scraper.py

@@ -9,6 +9,8 @@ import urllib2
 
 import lxml.html
 
+from collections import deque
+
 STRIP_NEWLINES = (lambda x: re.sub('\n', ' ', x.strip()))
 STRIP_HTML_TAGS = (lambda x: re.sub(r'<.*?>', '', x.strip()))
 SEARCH = (lambda x,y: re.search(x, y).group(1).strip())
@@ -17,23 +19,23 @@ def write_status(status_msg):
    sys.stdout.write('\r%s' % status_msg)
    sys.stdout.flush()
 
-def throttle_sleep():
+def throttle_sleep(sleep_time):
    write_status("going to sleep for a bit...")
-   time.sleep(3)
+   time.sleep(sleep_time)
    write_status("time to get back to work!")
 
 class plos_connection(object):
    def __init__(self):
       self.base_url = ('http://www.ploscompbiol.org')
       self.seed_url = ('/article/browse.action?field=on&pageSize=10&' +
-                       'startPage=2&selectedSubjects=Computational+Biology')
+                       'startPage=7&selectedSubjects=Computational+Biology')
 
    '''
       Send HTTP GET to the url 'page_url'. Returns the response to the HTTP
       GET.
    '''
-   def get_page(self, page_url):
-      throttle_sleep()
+   def get_page(self, page_url, sleep_time=2):
+      throttle_sleep(sleep_time)
 
       attempts = 0
       while (attempts < 5):
@@ -42,8 +44,11 @@ class plos_connection(object):
             return page_content
          except Exception as err:
             attempts += 1
-            sys.stderr.write('%s' % err)
-            sys.stderr.flush()
+
+            err_file = open('error.log', 'a')
+            err_file.write(('Error. Could not retrieve url "%s".\n%s\n') %
+                           (page_url, err))
+            err_file.close()
 
       return None
 
@@ -103,14 +108,28 @@ class plos_html_scraper(object):
 
       return article_text
 
+   def extract_references(self):
+      references = self.html_doc.cssselect('.references li')
+
+      ref_list = []
+      for reference in references:
+         ref_list.append(re.sub(r'\s+', ' ',
+                                re.sub(r'\n|Find this article online', '',
+                                       reference.text_content())))
+
+      return ref_list
+
    def extract_reference_links(self):
       references = self.html_doc.cssselect('.references li')
 
       ref_list = []
       for reference in references:
          link_list = reference.cssselect('.find')
+
[…]

### 2012-12-03 code/plos_scraper/directory_fixer_upper.pl
Deleting bad directories because they're obfuscating the good ones

@@ -35,6 +35,8 @@ sub dir_map {
 }
 
 sub hoist_references {
+   my ($REF_ROOT) = @_;
+
    opendir(my $REF_DIR, getcwd()) or croak('Unable to open current directory');
 
    my $DIR_BEGIN = telldir($REF_DIR);
@@ -42,7 +44,7 @@ sub hoist_references {
    # A loop to pull all sub directories up to current directory
    for my $sub_dir (read_dir($REF_DIR)) {
       dir_map($sub_dir, sub {
-         hoist_references();
+         hoist_references($REF_ROOT);
       });
    }
    closedir($REF_DIR);
@@ -71,11 +73,12 @@ sub fix_ref_dir {
    my ($paper_dir) = @_;
 
    my $success = dir_map("$paper_dir/references", sub {
-      opendir(my $REF_DIR, getcwd()) or croak('Unable to open cwd');
+      my $reference_root = getcwd();
+      opendir(my $REF_DIR, $reference_root) or croak('Unable to open cwd');
 
       for my $sub_dir (read_dir($REF_DIR)) {
          dir_map($sub_dir, sub {
-            hoist_references();
+            hoist_references($reference_root);
          });
       }
       closedir($REF_DIR);

### 2012-12-03 code/plos_scraper/scraper.py

@@ -283,9 +283,9 @@ def fetch_plos_references(plos_conn, ref_dir, doc_parser, ref_ndx=0):
       pubmed_html = plos_conn.get_page(pubmed_page)
       if (pubmed_html is None): continue
 
-      ref_dir = os.path.join(ref_dir, '%s' % ref_ndx)
-      if (not os.path.exists(ref_dir)):
-         os.makedirs(ref_dir)
+      sub_ref_dir = os.path.join(ref_dir, '%s' % ref_ndx)
+      if (not os.path.exists(sub_ref_dir)):
+         os.makedirs(sub_ref_dir)
 
       # each pubmed doc meta dictionary consists of 3 keys:
       # title, authors, abstract
@@ -299,12 +299,12 @@ def fetch_plos_references(plos_conn, ref_dir, doc_parser, ref_ndx=0):
          err_file.close()
 
       # create and populate meta data for the reference
-      ref_meta_file = open(os.path.join(ref_dir, 'meta.txt'), 'w+')
+      ref_meta_file = open(os.path.join(sub_ref_dir, 'meta.txt'), 'w+')
       ref_meta_file.write(generate_ref_meta(pubmed_meta).encode('utf-8'))
       ref_meta_file.close()
 
       # create and populate text for the reference
-      text_file = open(os.path.join(ref_dir, 'paper.txt'), 'w+')
+      text_file = open(os.path.join(sub_ref_dir, 'paper.txt'), 'w+')
       text_file.write(generate_ref_text(pubmed_meta).encode('utf-8'))
       text_file.close()
 

### 2012-12-03 code/citer/citer.py
ignore citations where the reference is missing

@@ -46,7 +46,7 @@ def fullTest():
          res.append(normalRun(paper))
       except OSError:
          print "Error parsing paper: " + paperName
-         next
+         continue
 
    res = sorted(res, reverse = True)
    for paper in res:
@@ -66,7 +66,7 @@ def normalRun(paper):
 
       # Skip citations that do not have a reference.
       if not paper.references.has_key(correctReference):
-         next
+         continue
 
       total += 1
 
@@ -82,9 +82,7 @@ def normalRun(paper):
                misses += 1
             break
 
-   #print "{} (Hits: {}, Misses: {}, Total: {}) -- {}".format((float(hits) / total), hits, misses, total, paper.title)
-   #print "{:.2%}\t(Hits: {},\tMisses: {},\tTotal: {})\t-- {}".format((float(hits) / len(paper.citations)), hits, misses, len(paper.citations), paper.title)
-   return ((float(hits) / len(paper.citations)), "{:.2%}\t(Hits: {},\tMisses: {},\tTotal: {})\t{}".format((float(hits) / len(paper.citations)), hits, misses, len(paper.citations), paper.title))
+   return ((float(hits) / total), "{:.2%}\t(Hits: {},\tMisses: {},\tTotal: {})\t{}".format((float(hits) / total), hits, misses, total, paper.title))
 
 
 # This one runs all the mothods in isolation and then tries to give a suggested ordering.
@@ -103,7 +101,7 @@ def orderingRun(paper):
 
          # Skip citations that do not have a reference.
          if not paper.references.has_key(correctReference):
-            next
+            continue
 
          guess = methodObj.guess(cite, paper)
          if guess == correctReference:
@@ -133,7 +131,7 @@ def debugRun(paper):
       # Skip citations that do not have a reference.
       if not paper.references.has_key(correctReference):
          print "Warning: There is no citation information found for citation #{}, skipping".format(correctReference)
-         next
+         continue
 
       print '---------'
       print cite.paragraphContext.raw

### 2012-12-03 code/citer/citer.py
Allowing multiple cites next to eachother to be interchanged.

@@ -65,7 +65,7 @@ def normalRun(paper):
       correctReference = paper.citationKey[i]
 
       # Skip citations that do not have a reference.
-      if not paper.references.has_key(correctReference):
+      if not paper.references.has_key(correctReference['main']):
          continue
 
       total += 1
@@ -76,7 +76,7 @@ def normalRun(paper):
       for methodObj in methods:
          guess = methodObj.guess(cite, paper)
          if guess:
-            if guess == correctReference:
+            if guess in correctReference['allowed']:
                hits += 1
             else:
                misses += 1
@@ -100,11 +100,11 @@ def orderingRun(paper):
          correctReference = paper.citationKey[i]
 
          # Skip citations that do not have a reference.
-         if not paper.references.has_key(correctReference):
+         if not paper.references.has_key(correctReference['main']):
             continue
 
          guess = methodObj.guess(cite, paper)
-         if guess == correctReference:
+         if guess in correctReference['allowed']:
             hits += 1
          elif guess:
             misses += 1
@@ -129,8 +129,8 @@ def debugRun(paper):
       correctReference = paper.citationKey[i]
 
       # Skip citations that do not have a reference.
-      if not paper.references.has_key(correctReference):
-         print "Warning: There is no citation information found for citation #{}, skipping".format(correctReference)
+      if not paper.references.has_key(correctReference['main']):
+         print "Warning: There is no citation information found for citation #{}, skipping".format(correctReference['main'])
          continue
 
       print '---------'
@@ -146,13 +146,13 @@ def debugRun(paper):
          res += methodObj.__class__.__name__ + "(" + str(guess) + '), '
          if not reportedValue and guess:
             reportedValue = True
-            if guess == correctReference:
+            if guess in correctReference['allowed']:
                hits += 1
             else:
                misses += 1
 
       print res
-      print "Actual Reference: {0}".format(correctReference)
+      print "Actual Reference: {0}".format(correctReference['allowed'])
       print '---------'
 
    print "HITS: {0} / {1} ({2})".format(hits, len(paper.citations), hits / float(len(paper.citations)))

### 2012-12-03 code/citer/parser.py

@@ -81,6 +81,9 @@ def parseCitations(entry):
          replacement += '[{0}]'.format(number)
       parsedText = parsedText.replace(cite, replacement)
 
+   # TODO(eriq): Catch ranges and expand them.
+   # [1]-[5] => [1][2][3][4][5]
+
    # Go line by line.
    for line in parsedText.splitlines():
       rawLine = line.strip()
@@ -99,7 +102,6 @@ def parseCitations(entry):
 
          for cite in cites:
             citeNum = int(re.search('(\d+)', cite).group(1))
-            citationKey.append(citeNum)
 
             markedLine = rawLine.replace(cite, MARKED_CITATION_MARKER)
             markedLine = re.sub('\[\s*\d+\s*\]', CITATION_MARKER, markedLine)
@@ -126,6 +128,17 @@ def parseCitations(entry):
             markedSentence = rawSentence.replace(cite, MARKED_CITATION_MARKER)
             markedSentence = re.sub('\[\s*\d+\s*\]', CITATION_MARKER, markedSentence)
             citesPerSentence = len(re.findall('\[\s*\d+\s*\]', rawSentence))
+
+            # Allow all cites in the sentence that are not seperated by a word character to be
+            # allowed as a correct citation.
+            # So things like [1][2][3] and [1],[2],[3] can be caught
+            correctCitations = set([citeNum])
+            match = re.search('(?:\[\s*\d+\s*\]\W*)*{}(?:\w*\[\s*\d+\s*\])*'.format(re.escape(cite)), rawSentence)
+            if match and match.group(0) != cite:
+               adjacentCites = re.findall('\[\s*\d+\s*\]', match.group(0))
+               for adjacentCite in adjacentCites:
+                  correctCitations.add(int(re.search('(\d+)', adjacentCite).group(1)))
+            citationKey.append({'main': citeNum, 'allowed': correctCitations})
 
             citations.append(Citation(rawLine, noCitationsLine,
                                       noNumbersLine, markedLine,

### 2012-12-03 code/citer/citer.py
Expanded citation ranges

@@ -49,8 +49,11 @@ def fullTest():
          continue
 
    res = sorted(res, reverse = True)
+   total = 0
    for paper in res:
       print paper[1]
+      total += paper[0]
+   print "Total: {}".format(total / len(res))
 
 def normalRun(paper):
    methods = [ method(paper) for method in AVAILABLE_METHODS ]

### 2012-12-03 code/citer/parser.py

@@ -71,8 +71,9 @@ def parseCitations(entry):
    # For when we see the references
    noMoreCitations = False
 
-   # First, make a global replacement for multiple cites eg. '[1, 2]'
    parsedText = entry['fullText']
+
+   # First, make a global replacement for multiple cites eg. '[1, 2]' => '[1][2]'
    groupedCitations = re.findall('\[\s*\d+\s*(?:,\s*\d+\s*)+\]', parsedText)
    for cite in groupedCitations:
       numbers = re.findall('\d+', cite)
@@ -81,8 +82,19 @@ def parseCitations(entry):
          replacement += '[{0}]'.format(number)
       parsedText = parsedText.replace(cite, replacement)
 
-   # TODO(eriq): Catch ranges and expand them.
+   # Expand citation ranges.
    # [1]-[5] => [1][2][3][4][5]
+   ranges = re.findall('\[\s*\d+\s*\]\s*\-\s*\[\s*\d+\s*\]', parsedText)
+   for citeRange in ranges:
+      numbers = re.findall('\d+', citeRange)
+      if len(numbers) != 2:
+         print "WARNING: A range of non-two length was found (" + citeRange + "). No replacement will occur."
+         continue
+
+      replacement = ''
+      for number in range(int(numbers[0]), int(numbers[1]) + 1):
+         replacement += '[{0}]'.format(number)
+      parsedText = parsedText.replace(citeRange, replacement)
 
    # Go line by line.
    for line in parsedText.splitlines():

### 2012-12-03 paper/paper.tex
Adding the outline of the paper

% Paper for CSC580 final project.
\documentclass[10pt, conference, compsocconf]{IEEEtran}

\usepackage{float}
%\usepackage{url}
\usepackage{graphicx}
\usepackage{subfig}
\usepackage{color}

\begin{document}

\title{Citeopotamus}

% author names and affiliations
% use a multiple column layout for up to two different
% affiliations

\author{\IEEEauthorblockN{Eriq Augustine, Aldrin Montana, Ryan Verdon}
\\
\IEEEauthorblockA{Department of Computer Science\\
Cal Poly, San Luis Obispo\\
 \textsf{\{eaugusti, amontana, rverdon\}@calpoly.edu}
}
}

\maketitle

\thispagestyle{empty}
\pagestyle{empty}

\section{Introduction}\label{sec:introduction}
%problem statement
%The whole problem of recommending citations
%Discuss the two situations we are attacking

\section{Contributions}\label{sec:contributions}
%dataset
%Citation matching methods

\section{Dataset}\label{sec:dataset}
%overview
%different components of the data
%implementation
%Metrics - #papers, #references, etc

\section{Architecture}\label{sec:architecture}

\section{Parsing}\label{sec:parsing}
%transformations
%contexts

\section{Methods}\label{sec:methods}

\section{Results}\label{sec:results}

\section{Future Work}\label{sec:future}

\section{Related Work}\label{sec:related}

\section{Conclusion}\label{sec:conclusion}

\section{Thanks}

\bibliographystyle{acm}
\bibliography{refs}

\end{document}

### 2012-12-04 paper/paper.tex
Adding rough draft of the lame parts. They obviously still need work.

@@
 \section{Introduction}\label{sec:introduction}
-%problem statement
-%The whole problem of recommending citations
-%Discuss the two situations we are attacking
+The problem of recommending citations for a technical paper is known and has many approaches to attempt to solve it.\cite{cite1,cite2,cite3,cite4,cite5,cite6,cite7,cite8} Solutions range from graph based social network approaches to language models to match meaning in both the paper and the recommended text.
+But the problem of recommending where inside the paper to put citations is unknown.
+The ideal solution would recommend an exact spot in the paper to put a specific citation.
+To solve this problem there exist two separate pieces.
+First, given a location of a citation the solution must be able to examine the references for the paper and choose the most appropriate citations.
+Second, find locations where citations should go. We leave the second problem to be done in the future while we focus on solving the first in this paper.
+
+The rest of the paper is laid out as follows. Section \ref{sec:contributions} is about what we are contributing. The following section describes
+out testing dataset. We then talk about our architecture we created to solve the problem. Then we go into how we parse papers and
+discuss the methods for choosing the best citation. Then we go into future work, related work, and lastly our conclusion.
 
 \section{Contributions}\label{sec:contributions}
-%dataset
-%Citation matching methods
+Our contributions consist of a dataset to test new solutions and methods to recommend citations given a location for a citation.
 
@@
 \section{Future Work}\label{sec:future}
+We believe this work can be continued on in a couple obvious directions.
+The most obvious is to tackle the second part of the problem we mentioned early in the paper.
+That is the case where the solution must automatically look through the document to find places that need citations.
+The next most obvious extension is to improve our methods for recommending citations.
+New ways of comparing the context of a location for a citation and all of the papers available for citations are needed.
+Something that would be interesting to examine is summarizing every possible citation paper and treat the summarization as another abstract to use in our pipeline.
+The hardest and most interesting extension
+of this work would be to tie the solution in with a citation recommendation solution. We feel that would be an awesome advance in paper writing.
 
 \section{Related Work}\label{sec:related}
+We were unable to find any related work on recommending citations given a spot for a citation to go.
+Unlike the problem of recommending citations for a paper.
+Copious amounts of work already exists on the topic.
+With several different approaches.
+One of the most common was using models to compare a paper and the rest of the dataset.
+Some of the models used includes translation models, probabilistic models, and several forms of LDAs.\cite{cite1, cite2, cite3} The next most common group of solutions was to use citations graphs to recommend missing citations.\cite{cite6} One group extended the notion of graphs and included metadata to help filter out results.\cite{cite4} One of the most
+interesting and unique approaches was to not look at co-citations but to look at co-accesses via logs like HTTP access records.\cite{cite7} 
+Another interesting approach used collaborative filtering to let communities help decide citations.\cite{cite8} For more related work in
+citation recommendation we recommend the survey by McNee et al. they go into a lot of depth on the problem and common pitfalls.\cite{cite5}
 
@@
 \section{Thanks}
+We thanks the folks at PLOS for providing the source of our dataset. Without them this would of been a lot harder.
 

### 2012-12-06 code/plos_scraper/directory_fixer_upper.pl
These scripts are totally good for fixing problems and getting reference stats (won't need this one anymore but I don't want to just delete it in cold blood).
w00h.

@@ -6,7 +6,7 @@ use Carp;
 use Cwd;
 use File::Copy;
 
-use constant ROOT_DIR => getcwd().'/data/';
+use constant ROOT_DIR => getcwd().'/fix_data/';
 
 sub dir_status {
    if ($ENV{DEBUG}) {
@@ -17,7 +17,7 @@ sub dir_status {
 sub read_dir {
    my ($dir_handle) = @_;
 
-   return grep { $_ !~ m/[.]+/ } readdir($dir_handle);
+   return grep { $_ !~ m/^[.]/ } readdir($dir_handle);
 }
 
 sub dir_map {
@@ -35,59 +35,50 @@ sub dir_map {
 }
 
 sub hoist_references {
-   my ($REF_ROOT) = @_;
+   my ($num_files, $ref_root) = (0, @_);
 
-   opendir(my $REF_DIR, getcwd()) or croak('Unable to open current directory');
+   opendir(my $CURR_DIR, getcwd()) or croak('Unable to open current directory');
 
-   my $DIR_BEGIN = telldir($REF_DIR);
-
-   # A loop to pull all sub directories up to current directory
-   for my $sub_dir (read_dir($REF_DIR)) {
-      dir_map($sub_dir, sub {
-         hoist_references($REF_ROOT);
-      });
-   }
-   closedir($REF_DIR);
-
-   opendir($REF_DIR, getcwd()) or croak('Unable to open current directory');
-
-   for my $sub_dir (read_dir($REF_DIR)) {
+   for my $sub_dir (read_dir($CURR_DIR)) {
+      $num_files++;
       if (-d $sub_dir) {
-         my ($abs_sub_dir, $parent_dir) = (getcwd()."/$sub_dir", getcwd().'/..');
-         print("move '$abs_sub_dir' '$parent_dir\n'");
+         if (chdir($sub_dir)) {
+            my $has_files = hoist_references($ref_root);
+            chdir(q{..});
 
-         if (!$ENV{DEBUG}) {
-            #move($abs_sub_dir, $parent_dir) or croak("error moving file: $!");
-            `mv "$abs_sub_dir" "$parent_dir"`;
-            #print `pwd`;
-            #print `ls`;
+            if (!$has_files) {
+               dir_status();
+               if ($ENV{DEBUG}) { print "rm -rf $sub_dir\n"; }
+               else { `rm -rf $sub_dir`; }
+               next;
+            }
+         }
+
+         if (!-d "$ref_root/$sub_dir") {
[…]

### 2012-12-06 code/plos_scraper/reference_stats.pl

@@ -1,0 +1,170 @@
+#!/usr/bin/perl
+use strict;
+use warnings;
+
+use Carp;
+use Cwd;
+use File::Copy;
+
+use constant ROOT_DIR => getcwd().'/data/';
+
+sub dir_status {
+   if ($ENV{DEBUG}) {
+      print("current directory: ".getcwd()."\n");
+   }
+}
+
+sub read_dir {
+   my ($dir_handle) = @_;
+
+   return grep { $_ !~ m/[.]+/ } readdir($dir_handle);
+}
+
+sub dir_map {
+   my ($success, $dir_name, $anon_func) = (0, @_);
+
+   if (-d $dir_name && chdir($dir_name)) {
+      dir_status();
+      &$anon_func();
+      $success = 1;
+      chdir(q{..});
+      dir_status();
+   }
+
+   return $success;
+}
+
+sub get_ref_stats {
+   my ($REF_ROOT, $max_citation, $num_citations) = @_;
+   my ($global_max, $global_count) = (0, 0);
+
+   opendir(my $REF_DIR, getcwd()) or croak('Unable to open current directory');
+
+   my $DIR_BEGIN = telldir($REF_DIR);
+
+   # A loop to pull all sub directories up to current directory
+   for my $sub_dir (read_dir($REF_DIR)) {
+      dir_map($sub_dir, sub {
+         my ($tmp_max, $tmp_count) = get_ref_stats($REF_ROOT, $max_citation, $num_citations + 1);
+         #print("max ref: $tmp_max\ncitation count: $tmp_count\n");
+
+         if ($global_max < $tmp_max) { $global_max = $tmp_max; }
+         if ($global_count < $tmp_count) { $global_count = $tmp_count; }
+      });
+   }
+   closedir($REF_DIR);
+
+   opendir($REF_DIR, getcwd()) or croak('Unable to open current directory');
+
+   my $sub_dir_name = q{};
+   for my $sub_dir (read_dir($REF_DIR)) {
+      if (-d $sub_dir) {
+         $sub_dir_name = $sub_dir;
+
+         if ($sub_dir_name =~ m/\/(\d+)$/) {
+            my $dir_name = $1;
+            #print ("dir name: $dir_name\n");
+
+            if ($max_citation < $dir_name) {
+               $max_citation = $dir_name;
+            }
+         }
+
+      }
+   }
+
+   closedir($REF_DIR);
+
+   if ($global_max < $max_citation) { $global_max = $max_citation; }
[…]

### 2012-12-07 code/citer/citer.py
Implemented Foaads metric

@@ -7,6 +7,8 @@ from constants import DEBUG
 import method
 import parser
 
+DATA_DIR = '../data'
+
 AVAILABLE_METHODS = [
                      method.PreContextTitleAuthorMethod,
                      method.SentenceTitleAuthorMethod,
@@ -38,12 +40,20 @@ def main():
 
 def fullTest():
    res = []
-   for paperName in os.listdir('../data'):
+   allHitRefs = set()
+   allRefs = set()
+
+   for paperName in os.listdir(DATA_DIR):
       paper = None
 
       try:
-         paper = parser.parseFullDataset('../data/' + paperName)
-         res.append(normalRun(paper))
+         paper = parser.parseFullDataset(DATA_DIR + '/' + paperName)
+         paperRes = normalRun(paper)
+
+         allHitRefs.update(paperRes[2])
+         allRefs.update([ ref.title.strip().upper() for ref in paper.references.values()])
+
+         res.append((paperRes[0], paperRes[1]))
       except OSError:
          print "Error parsing paper: " + paperName
          continue
@@ -53,7 +63,14 @@ def fullTest():
    for paper in res:
       print paper[1]
       total += paper[0]
-   print "Total: {}".format(total / len(res))
+   print "Average: {}".format(total / len(res))
+   if len(res) % 2 == 0:
+      print "Median: {}".format((res[len(res) / 2][0] + res[len(res) / 2 - 1][0]) / 2.0)
+   else:
+      print "Median: {}".format(res[len(res) / 2][0])
+
+   print "Hit Refs: {}, All Refs: {}".format(len(allHitRefs), len(allRefs))
+   print "Foaad Metric: {}".format(float(len(allHitRefs)) / len(allRefs))
 
 def normalRun(paper):
    methods = [ method(paper) for method in AVAILABLE_METHODS ]
@@ -62,6 +79,9 @@ def normalRun(paper):
    misses = 0
    # Don't count references without any information
    total = 0
+
+   # foaad counting system
+   hitRefs = set()
 
    for i in range(0, len(paper.citations)):
       cite = paper.citations[i]
@@ -81,12 +101,14 @@ def normalRun(paper):
          if guess:
             if guess in correctReference['allowed']:
                hits += 1
+               hitRefs.add(paper.references[guess].title.strip().upper())
             else:
                misses += 1
             break
 
[…]

### 2012-12-07 paper/paper.tex
Working on paper

@@
 \section{Architecture}\label{sec:architecture}
+The Citeopotamus system is broken into two independent parts, the scrapper and citer.
+The general architecture can be seen in Figure \ref{fig:arch}.
+
+\begin{figure*}[ht]
+   \includegraphics[width=\textwidth px]{images/arch.eps}
+        \caption{The Citeopotamus architecture overlaid on a hippopotamus.}
+        \label{fig:arch}
+\end{figure*}
+
+\subsection{Scraper}
+TODO(aldrin)
+
+\subsection{Structured Paper Directory Format}
+The output of the scraper is a directory that contains information about the root paper and all the reference that were collected.
+To make all the information easily accessible to anyone without imposing any arbitrary restrictions, the structure of the
+data is enforced by directory structure.
+
+The root directory is named using the root paper's title. Inside the root directory is a ``references'' directory.
+Inside the ``references'' directory are sub-directories named with the number of that citation. A missing directory
+means that the scraper could not collect that reference's information.
+
+Every directory that represents a paper will have at most four files:
+\begin{enumerate}
+   \item meta.txt -- Contains the title, authors, tags, categories, and abstract. This is the only required file.
+   \item paper.pdf -- The pdf version of the paper.
+   \item paper.txt -- The text version of the paper.
+   \item refs.txt -- Only the references that appear at the bottom of the paper. This information is duplicated in paper.txt, but placed here for convenience.
+\end{enumerate}
+
+A sample directory structure can be seen in Figure \ref{fig:tree}.
+
+\begin{figure}[ht]
+   \includegraphics[width=\columnwidth px]{images/tree.eps}
+        \caption{The structure of a paper directory.}
+        \label{fig:tree}
+\end{figure}
+
+\subsection{Citer}\label{sec:archCiter}
+The citer begins by attempting to parse a directory structure into a structured collection of papers.
+The citer then pre-processed each paper and generates a set of contexts (see Section \ref{sec:context}) for each citation in each
+root paper.
+
+After all of the contexts are generated, those contexts are fed into the Method Pipeline. In this pipeline are all the methods (see Section \ref{sec:methods})
+that operate on the contexts to try and generate citations. Each citation in put through each method one at a time. If any method emits a value, then the pipeline
+it short circuited and the emitted value is used as the citation. Because of this short circuiting behavior, the methods in the pipeline are ordered by approximate
+precision. That is, all of the methods that rarely miss (regardless of how many citations they correctly place) are moved to the front of the pipeline.
+As a citation travels through the pipeline, its citation becomes more and more uncertain.
 
@@
 %contexts
+\label{sec:context}
 
@@
 \section{Future Work}\label{sec:future}
+TODO(eriq): THis section is bad.
 We believe this work can be continued on in a couple obvious directions.
@@
 of this work would be to tie the solution in with a citation recommendation solution. We feel that would be an awesome advance in paper writing.
+
+\subsection{Improvements}
+
+\subsubsection{Pipeline Uncertianty}
+As mentioned in Section \ref{sec:archCiter}, the further a citation moves into the pipeline the more uncertain its guessed citation becomes.
+Incorporating this uncertainty into the information provided to the user can be very useful in a real-world system.
+
+\subsection{Future Product}
 

### 2012-12-07 paper/paper.tex
Working on paper

@@
 
+\subsubsection{Structure of Paper Text}
+%TODO(aldrin): Expand here if necessary
+If the paper text was generated from OCR, then the structure of the text was left up to the OCR engine.
+However, papers scraped from PLOS were in HTML and extra formatting can be infered.
+
+All text inside top-level $p$ tags can be infered to be an entire paragraph and was placed on a single line.
+The references section was seperated from the rest of the paper by a single line with only ``REFERENCES'' on it.
+
 \subsection{Structured Paper Directory Format}
@@
 \begin{enumerate}
-   \item meta.txt -- Contains the title, authors, tags, categories, and abstract. This is the only required file.
+   \item meta.txt -- Contains the title, authors, tags, categories, and abstract. This is the only file required for every paper directory.
    \item paper.pdf -- The pdf version of the paper.
-   \item paper.txt -- The text version of the paper.
+   \item paper.txt -- The text version of the paper. This file is required for the root paper.
    \item refs.txt -- Only the references that appear at the bottom of the paper. This information is duplicated in paper.txt, but placed here for convenience.
@@
 \section{Parsing}\label{sec:parsing}
-%transformations
-%contexts
-\label{sec:context}
+Because of its recursive nature, parsing the directory sreucture itself is rather simple.
+Parsing the text of a paper however, can be quite complex.
+
+\subsection{OCR}
+Before any parsing can be done a paper, it must first be converted to a plain text (UTF-8) format.
+Since PLOS provides most of their papers in an HTML format, this only had to be done offline for a few
+papers. After looking at many alternatives, we chose to use ABBYY Finereader 10\cite{abbyy}. This
+is a comercial OCR product, and requires a lisence to use.
+
+ABBYY Finereader clearly outperformed all of the other OCR products we tried. It is especially
+good at maintaining and recognizing formatting. Many other OCR products failed to correctly parse
+two-column formats and thus generated unusable output.
+
+\subsection{Transformations}
+Before parsing the text of the paper, we had to make some global transformation on the paper.
+Most of these transformations were done with simple regular expressions.
+
+\subsubsection{Multiple Citations}
+It is not unheard of for authors to make multiple citations within the same brackets: $$[1, 2]$$
+These have to be parsed out and replaced with individual citations next to eachother: $$[1][2]$$
+
+\subsubsection{Ranges}
+It is very common for authors to cite entire ranges at a time: $$[1] - [3]$$
+This is especially seen when an author is referencing background material. These ranges must be expanded out to
+the fill listof citations: $$[1][2][3]$$
+
+\subsubsection{False Positive Sentence Enders}\label{sec:fpEnders}
+Being able to split up paragraphs into sentences is very important to the Citeopotamus system.
+We first tried to use NLTK's \textit{PunktSentenceTokenizer}. However, this did not seem to work well.
+It seemed to have a problem with some of the symbols used in acedemic papers, such as the square brackets around
+citations. To combat the punctuation tokenizing problem, we decided to only spolit sentnce on periods, question marks, and
+exclamations points. Additionally, we replaced common false positive sentence enters i.e.
+$$i.e. => \_ie\_$$
+$$dr. => \_dr\_$$
+$$0.05 => \_0\_05\_$$
+
+Using this tactic, there is a chance that a real sentence ender is replaced. However, this will still
+include the original sentence in the result and the original sentence will still be located closer to the
+citation that the incorrectly included sentence. Missing a significant portion of a sentence would be a much more
+grevious error because then the context required to identify the citation may be missing.
+
+\subsection{Contexts}\label{sec:context}
+Contexts are the core of the Citeopotamus system. A ``context'' is just the words surrounding the citation.
+Deciding which words to include in a context is very important. We use three different types of contexts that are meant for different
+levels of precision. The contexts that include more words tends to be less precise and will therefore appear later in the pipeline.
+However, these larger contexts have access to more information than the smaller ones and can sometimes makes guesses that are impossible
+(outside of random) to the smaller contexts.
+
+\subsubsection{Paragraph}
+The largest of the contexts. We do not consider anything larger because it is very rare for an author to include information about a citation
+outside of the paragrapgh that the citation is in (not including parsing or OCR formatting errors). Paragraphs are easy to parse because the
+scraper puts one paragraph per line.
+
+\subsubsection{Sentence}
+Sentence level contexts contain just the sentence that the citation was main in. As discussed in Section \ref{sec:fpEnders},
+sentence context is parsed just by splitting the paragraph on sentence ending punctuation after false positives have been replaced.
+
+\subsubsection{Clause}
+Clause context is the smallest and most complex context. The purpose of this context is to capture the clause that the citation was made in.
+There are two parts to parsing this context: looking for parenthesis and walking backwards in the sentence.
+
+We will use the following actual sentence as a running example:
+\begin{quote}
+In previous work, the Guyton models were modularized and re-implemented in Fortran, C++ (M2SL \textbf{[]}), and Simulink \textbf{[]}.
+\end{quote}
+
+When trying to find the context of the first citaion, we recognize that it is surrounded by parenthesis.
+We take the parenthesis as a hint the that content inside the parenthesis is more related to the citation than the surrounding words.
+
+If there are no parethesis surrounding the citaion (as with the second citation), then we begin walking backwards in the sentence from the citation.
+We will continue walking backwards in the sentence until we find:
+\begin{enumerate}
+   \item The beginning of the sentence.
+   \item Another citation.
+   \item A character that may break a clause: '[', ']', '.', ',', ';', ':', '!', '"', '?', or '-'.
+\end{enumerate}
+
+We do not include the words that appear after the citation because we want to avoid a clause context expanding into a sentence context and
+in English, information about a reference is usually presented before the citation.
+
+Our example would generate two clause contexts:
+\begin{quote}
+M2SL
+\end{quote}
+
+\begin{quote}
+and Simulink
+\end{quote}
+
+Note that both cases generate contexts that contain the name of the product featured in the paper and no erronous inforamtion. Whereas the
+sentence context not only contains both produces, but a slew of other seemingly important words: ``Guyton'', ``Fortran'', and ``C++''.
+
+\subsection{References}
 
 \section{Methods}\label{sec:methods}
+
+\subsection{History}
+
+\section{Evaluation}
+
+\subsection{Adjacent Citations}
+%[][]; [], []
 
@@
 \subsection{Improvements}
+
+\subsubsection{Parsing and Scraping}
+Parsing is vital to the Citeopotamus system. If a context is inproperly parsed, then everything else around that citation falls apart.
+A spot check of papers that perform poorly (under 10\%) reveals that many of these these papers have many incorectly parsed contexts.
+Some of these errors come from an error in parsing like missing a false positive sentence ender. However, most of these errors appear to
+come from difficulties scraping the paper. We believe that irregularities in the paper's HTML causes poor formatting of the resulting
+plain text paper and therefore causes parsing errors.
 

### 2012-12-07 code/citer/paper.py

@@ -91,7 +91,7 @@ class Citation:
       if match:
          self.preContext = match.group(1).replace(parser.MARKED_CITATION_MARKER, ' ').strip()
       else:
-         match = re.search('([^\[\]\.,;:!"\-]+){}'.format(re.escape(parser.MARKED_CITATION_MARKER)), markedSentence)
+         match = re.search('([^\[\]\.,;:!"\?\-]+){}'.format(re.escape(parser.MARKED_CITATION_MARKER)), markedSentence)
 
          if match:
             self.preContext = match.group(1).strip()

### 2012-12-07 code/citer/parser.py

@@ -122,12 +122,16 @@ def parseCitations(entry):
             # 'e.g.', 'mr.', etc.
             # This may accidentally join extra sentences, but it is better than too short sentences.
             # This could be done in one, but it looks ugly and it should be fine.
-            hackLine = re.sub('e\.?g\.', '_eg_', rawLine, flags=re.IGNORECASE)
-            hackLine = re.sub('dr\.', '_dr_', hackLine, flags=re.IGNORECASE)
-            hackLine = re.sub('mr\.', '_mr_', hackLine, flags=re.IGNORECASE)
-            hackLine = re.sub('mrs\.', '_mrs_', hackLine, flags=re.IGNORECASE)
-            hackLine = re.sub('ms\.', '_ms_', hackLine, flags=re.IGNORECASE)
-            hackLine = re.sub('mme\.', '_mme_', hackLine, flags=re.IGNORECASE)
+            hackLine = re.sub(r'\be\.?g\.', '_eg_', rawLine, flags=re.IGNORECASE)
+            #hackLine = re.sub(r'\bi\.?e\.', '_ie_', rawLine, flags=re.IGNORECASE)
+            hackLine = re.sub(r'\bdr\.', '_dr_', hackLine, flags=re.IGNORECASE)
+            hackLine = re.sub(r'\bmr\.', '_mr_', hackLine, flags=re.IGNORECASE)
+            hackLine = re.sub(r'\bmrs\.', '_mrs_', hackLine, flags=re.IGNORECASE)
+            hackLine = re.sub(r'\bms\.', '_ms_', hackLine, flags=re.IGNORECASE)
+            hackLine = re.sub(r'\bmme\.', '_mme_', hackLine, flags=re.IGNORECASE)
+            hackLine = re.sub(r'\bet\.', '_et_', hackLine, flags=re.IGNORECASE)
+            hackLine = re.sub(r'\bal\.', '_al_', hackLine, flags=re.IGNORECASE)
+            hackLine = re.sub(r'\b(\d+)\.(\d+)', '_\1_\2_', hackLine, flags=re.IGNORECASE)
 
             rawSentence = re.search(
                   '(?:^|[\.\?!])\s*([^\.\?!]*' +

### 2012-12-07 paper/paper.tex
Working on paper

@@
 \section{Dataset}\label{sec:dataset}
+%TODO(aldrin)
 %overview
@@
 If the paper text was generated from OCR, then the structure of the text was left up to the OCR engine.
-However, papers scraped from PLOS were in HTML and extra formatting can be infered.
+However, papers scraped from PLOS were in HTML and extra formatting can be inferred.
 
-All text inside top-level $p$ tags can be infered to be an entire paragraph and was placed on a single line.
-The references section was seperated from the rest of the paper by a single line with only ``REFERENCES'' on it.
+All text inside top-level $p$ tags can be inferred to be an entire paragraph and was placed on a single line.
+The references section was separated from the rest of the paper by a single line with only ``REFERENCES'' on it.
 
-\subsection{Structured Paper Directory Format}
+\subsection{Structured Paper Directory Format}\label{sec:paperFormat}
 The output of the scraper is a directory that contains information about the root paper and all the reference that were collected.
@@
 \section{Parsing}\label{sec:parsing}
-Because of its recursive nature, parsing the directory sreucture itself is rather simple.
+Because of its recursive nature, parsing the directory structure itself is rather simple.
 Parsing the text of a paper however, can be quite complex.
@@
 Before any parsing can be done a paper, it must first be converted to a plain text (UTF-8) format.
-Since PLOS provides most of their papers in an HTML format, this only had to be done offline for a few
+Since PLOS provides most of their papers in an HTML format, this only had to be done off-line for a few
 papers. After looking at many alternatives, we chose to use ABBYY Finereader 10\cite{abbyy}. This
-is a comercial OCR product, and requires a lisence to use.
+is a commercial OCR product, and requires a licence to use.
 
@@
 
-\subsection{Transformations}
+\subsection{Transformations}\label{sec:transforms}
 Before parsing the text of the paper, we had to make some global transformation on the paper.
@@
 It is not unheard of for authors to make multiple citations within the same brackets: $$[1, 2]$$
-These have to be parsed out and replaced with individual citations next to eachother: $$[1][2]$$
+These have to be parsed out and replaced with individual citations next to each other: $$[1][2]$$
 
@@
 This is especially seen when an author is referencing background material. These ranges must be expanded out to
-the fill listof citations: $$[1][2][3]$$
+the fill list of citations: $$[1][2][3]$$
 
@@
 We first tried to use NLTK's \textit{PunktSentenceTokenizer}. However, this did not seem to work well.
-It seemed to have a problem with some of the symbols used in acedemic papers, such as the square brackets around
-citations. To combat the punctuation tokenizing problem, we decided to only spolit sentnce on periods, question marks, and
+It seemed to have a problem with some of the symbols used in academic papers, such as the square brackets around
+citations. To combat the punctuation tokenizing problem, we decided to only split sentence on periods, question marks, and
 exclamations points. Additionally, we replaced common false positive sentence enters i.e.
@@
 citation that the incorrectly included sentence. Missing a significant portion of a sentence would be a much more
-grevious error because then the context required to identify the citation may be missing.
+grievous error because then the context required to identify the citation may be missing.
 
@@
 The largest of the contexts. We do not consider anything larger because it is very rare for an author to include information about a citation
-outside of the paragrapgh that the citation is in (not including parsing or OCR formatting errors). Paragraphs are easy to parse because the
+outside of the paragraph that the citation is in (not including parsing or OCR formatting errors). Paragraphs are easy to parse because the
 scraper puts one paragraph per line.
@@
 
-When trying to find the context of the first citaion, we recognize that it is surrounded by parenthesis.
+When trying to find the context of the first citation, we recognize that it is surrounded by parenthesis.
 We take the parenthesis as a hint the that content inside the parenthesis is more related to the citation than the surrounding words.
 
-If there are no parethesis surrounding the citaion (as with the second citation), then we begin walking backwards in the sentence from the citation.
+If there are no parenthesis surrounding the citation (as with the second citation), then we begin walking backwards in the sentence from the citation.
 We will continue walking backwards in the sentence until we find:
@@
 
-Note that both cases generate contexts that contain the name of the product featured in the paper and no erronous inforamtion. Whereas the
+Note that both cases generate contexts that contain the name of the product featured in the paper and no erroneous information. Whereas the
 sentence context not only contains both produces, but a slew of other seemingly important words: ``Guyton'', ``Fortran'', and ``C++''.
 
-\subsection{References}
+\section{Methods}\label{sec:methods}
+All of our current methods use the same algorithm for determining the most appropriate reference for a citation.
+The difference in methods is the context and reference material that they choose to use.
+We use the full cross-product of contexts and reference materials in the final system.
 
-\section{Methods}\label{sec:methods}
+\subsection{Reference Material}
+The reference material is the text that is associated with the reference.
+The reference material that has the highest similarity to the context and surpassing the threshold is
+used as the guess for that citation.
+We use two different kinds of reference material: \textit{Reference Only} and \textit{Abstract}.
+
+\subsubsection{Reference Only}
+This reference material contains only information that is found in the reference section at the bottom of a paper.
+Note that for ease of parsing we take this information from the reference's meta information, and not the actual paper. However given
+some knowledge about how the references are formatted, it is trivial to parse out the title and authors.
+
+For this reference material we take the all the author names longer than two characters and the paper title.
+These words are then treated as unigrams.
+
+\subsubsection{Abstract}
+This reference material starts with the reference paper's abstract. However taking the entire abstract would include too many
+useless features, so we try to narrow it down some. We begin by removing all the stopwords from the abstract. We use
+the stopword list from the Onix Text Retrieval Toolkit\cite{stopwords}.
+
+The first set of features that we grab are all of the capital words in the abstract. The main idea here is to grab
+most of the ``important words'' in an abstract. A pronoun would be a very important word. The drawback of this method is that
+is will usually grab the first word in a sentence. This is mitigated by removing stopwords. The first word in a sentence
+is often the subject or a stopword (``The'', ``A'', etc).
+
+The second set of features we collect are the bigrams of the abstract, after stopword removal.
+
+To supplement the unigrams, we include any word that appears in any position of $\geq25\%$ of the bigrams.
+
+\subsubsection{Unique Sets}
+To help distinguish between the different references, we take all of the parsed reference material features and
+keep only features that appear in no more than two of the references. This way we can keep features that are somewhat
+unique, but get rid of features that occur too much.
 
 \subsection{History}
+It is rare for an author to cite the same paper twice in a paragraph. Even more rare for
+an author to cite the same paper twice in a sentence, and almost unheard of for an author to cite the
+same paper twice in the same clause. However, it is very common for there to be multiple citations
+made in the same context. To combat this, every method remembers every citation that it has given
+for each context in each paper. Since a method can remember its history, it can avoid making the
+same guess for a context.
+
+\subsection{Context Similarity}
+To compare the similarity between a context and the reference material, we use a Jaccardian Distance\cite{jaccard}.
 
 \section{Evaluation}
+To evaluate our system, we find the total number of references that we have successfully placed.
+
+Given $n$ papers $(p_{1}, p_{2}, p_{3} ..., p_{n})$. We will let $RF(n_{i})$ be the number of references
+for which we have full contextual information on and let $RT(n_{i})$ is the number of references
+that were correctly placed in the paper.
+
+Then we let our accuracy be:
+$$Accuracy = \frac{\sum_{i = 1}^{m} RF(p_{i})}{\sum_{i = 1}^{m} RT(p_{i})}$$
 
 \subsection{Adjacent Citations}
-%[][]; [], []
+While evaluating the results of a run, it is important to take into account \textit{adjacent citations}.
+These are citations that appear right next to each other without any content separating each other (``[][]'' and ``[], []''
+are both adjacent citation). We run into this situation often because we purposefully generate adjacent citations (see
+Section \ref{sec:transforms}).
+
+To deal with adjacent citations, we allow a citation guess to appear in any one of the adjacent positions.
 
 \section{Results}\label{sec:results}
+Because there are no other programs that attempt to do automated citation placement, we have no baseline to compare against.
+A random baseline would be inappropriate for this situation since there are is such a small chance of getting a correct
+citation when a paper has 50+ references.
+
+TODO(eriq): Table
 
 \section{Future Work}\label{sec:future}
-TODO(eriq): THis section is bad.
-We believe this work can be continued on in a couple obvious directions.
-The most obvious is to tackle the second part of the problem we mentioned early in the paper.
-That is the case where the solution must automatically look through the document to find places that need citations.
-The next most obvious extension is to improve our methods for recommending citations.
-New ways of comparing the context of a location for a citation and all of the papers available for citations are needed.
-Something that would be interesting to examine is summarizing every possible citation paper and treat the summarization as another abstract to use in our pipeline.
-The hardest and most interesting extension
-of this work would be to tie the solution in with a citation recommendation solution. We feel that would be an awesome advance in paper writing.
+There are many opportunities for future work in this project.
+Improving the actual implementation and increasing the scope of this project are both very plausible.
 
-\subsection{Improvements}
+\subsection{Implementation Improvements}
 
 \subsubsection{Parsing and Scraping}
-Parsing is vital to the Citeopotamus system. If a context is inproperly parsed, then everything else around that citation falls apart.
-A spot check of papers that perform poorly (under 10\%) reveals that many of these these papers have many incorectly parsed contexts.
+Parsing is vital to the Citeopotamus system. If a context is improperly parsed, then everything else around that citation falls apart.
+A spot check of papers that perform poorly (under 10\% accuracy) reveals that many of these these papers have many incorrectly parsed contexts.
 Some of these errors come from an error in parsing like missing a false positive sentence ender. However, most of these errors appear to
@@
 
-\subsubsection{Pipeline Uncertianty}
+\subsubsection{Pipeline Uncertainty}
 As mentioned in Section \ref{sec:archCiter}, the further a citation moves into the pipeline the more uncertain its guessed citation becomes.
@@
 
-\subsection{Future Product}
+\subsubsection{Context Similarity}
+Our current method for determining context similarity is very simplistic. A more complex algorithm that takes into account a word's distance to the
+citation may perform better.
+
+\subsubsection{Important Words}
+Currently, we very simplistically find words that we believe to be important in a sentence. Because these are the words that
+we compare to the reference material, choosing these words is key to guessing a citation. A very simple way to try and improve on this
+would be to use a parts of speech tagger to find all the proper nouns in a context. We did not use POS tagging because
+the NLTK POS taggers take too much time to run for the amount of gain it provides.
+
+Using synonym can also help finding important words.
+
+\subsection{Scope Increase}
+The first step to increasing the scope of this project would be to tackle the other problem discussed in the Introduction,
+guessing a citation given no information about where the citation appears.
+
+Once that step is complete, a citation placement engine can be turned into a citation recommendation system.
+The end goal would be a system where you can input your entire paper, and the system would recommend what papers
+you should be citing. This can be an invaluable tool when writing related works and background sections.
 
@@
 \section{Conclusion}\label{sec:conclusion}
+We have found that automatic citation placement is a difficult, but doable problem.
 

### 2012-12-07 code/citer/paper.py

@@ -97,3 +97,4 @@ class Citation:
             self.preContext = match.group(1).strip()
 
       self.preContextUnigrams = util.getNonStopNgrams(self.preContext, 1)
+      self.preContextBigrams = util.getNonStopNgrams(self.preContext, 2)

### 2012-12-07 paper/paper.tex
Committing my changes to the paper and then will merge Eriq's updated version.
Also changed the plos reference in refs.bib

--- 2012-12-07 paper/paper.tex
@@
 \section{Introduction}\label{sec:introduction}
-The problem of recommending citations for a technical paper is known and has many approaches to attempt to solve it.\cite{cite1,cite2,cite3,cite4,cite5,cite6,cite7,cite8} Solutions range from graph based social network approaches to language models to match meaning in both the paper and the recommended text.
-But the problem of recommending where inside the paper to put citations is unknown.
-The ideal solution would recommend an exact spot in the paper to put a specific citation.
-To solve this problem there exist two separate pieces.
-First, given a location of a citation the solution must be able to examine the references for the paper and choose the most appropriate citations.
-Second, find locations where citations should go. We leave the second problem to be done in the future while we focus on solving the first in this paper.
+The problem of recommending citations for a technical paper is known and has
+many approaches to attempt to solve it~\cite{cite1, cite2, cite3, cite4, cite5,
+cite6, cite7, cite8}. Solutions range from graph based social network
+approaches to language models to match meaning in both the paper and the
+recommended text. But the problem of recommending where inside the paper to put
+citations is unknown.  The ideal solution would recommend an exact spot in the
+paper to put a specific citation. To solve this problem there exist two
+separate pieces. First, given a location of a citation the solution must be
+able to examine the references for the paper and choose the most appropriate
+citations.  Second, find locations where citations should go. We leave the
+second problem to be done in the future while we focus on solving the first in
+this paper.
 
-The rest of the paper is laid out as follows. Section \ref{sec:contributions} is about what we are contributing. The following section describes
-out testing dataset. We then talk about our architecture we created to solve the problem. Then we go into how we parse papers and
-discuss the methods for choosing the best citation. Then we go into future work, related work, and lastly our conclusion.
+The rest of the paper is laid out as follows. Section \ref{sec:contributions}
+is about what we are contributing. The following section describes out testing
+dataset. We then talk about our architecture we created to solve the problem.
+Then we go into how we parse papers and discuss the methods for choosing the
+best citation. Then we go into future work, related work, and lastly our
+conclusion.
 
 \section{Contributions}\label{sec:contributions}
-Our contributions consist of a dataset to test new solutions and methods to recommend citations given a location for a citation.
+Our contributions consist of a dataset to test new solutions and methods to
+recommend citations given a location for a citation.
 
@@
 %overview
+The dataset for which we report results was collected from \textit{PLoS
+Computational Biology}~\cite{plos}. PLoS (Public Library of Science) is a
+nonprofit publisher that aims to accelerate progress in science. PLoS has
+several journals--ONE, Biology, Medicine, Genetics, Computational Biology,
+Pathogens, and Neglected Tropical Diseases--available to the public. For our
+purposes we collected articles from PLoS Computational Biology, the
+computational biology journal published by PLoS. We only collected articles
+from this journal simply for the reason that as computer scientists it is the
+most likely to be similar to computer science publications in style and in
+content. We initially were interested in a corpus of computer science
+publications, however we were unable to find a source that would allow us to
+programmatically collect computer science publications and articles.
+
 %different components of the data
-%implementation
-%Metrics - #papers, #references, etc
+From PLoS Computational Biology we collected a set of \textit{root papers}, the
+papers whose citations we attempt to correctly predict. For each root paper we
+attempted to retrieve all \textit{reference papers}, or papers listed in the
+reference section of the root paper. For each reference paper, we retrieve
+metadata of the paper--title and authors--and the abstract text. We prefer to
+get the full text of a reference paper, but unfortunately we were unable to
+retrieve these, and so we settled for paper abstracts. One of our main
+objectives for the data, which we mostly satisfied, was to collect what we
+refer to as \textit{complete papers}. A complete paper is a paper for which we
+could retrieve metadata and abstracts for all reference papers.
+
+In order to simplify our implementation, we maintain a particular structure of
+the articles collected from PLoS. This structure dictates how the articles are
+stored on disk (files with a particular format) and what data must be
+possessed. This structure is further described in sections
+\ref{sec:text_structure} and \ref{sec:dir_structure} below.
 

### 2012-12-07 paper/paper.tex
Added a table

--- 2012-12-07 paper/paper.tex
@@
 
-Given $n$ papers $(p_{1}, p_{2}, p_{3} ..., p_{n})$. We will let $RF(n_{i})$ be the number of references
-for which we have full contextual information on and let $RT(n_{i})$ is the number of references
-that were correctly placed in the paper.
+Given $n$ papers $(p_{1}, p_{2}, p_{3} ..., p_{n})$. We will let $RF(p_{i})$ be the number of references
+for which we have full contextual information on and let $RT(p_{i})$ is the number of references
+that were correctly placed in the paper $p_{i}$.
 
 Then we let our accuracy be:
-$$Accuracy = \frac{\sum_{i = 1}^{m} RF(p_{i})}{\sum_{i = 1}^{m} RT(p_{i})}$$
+$$Accuracy = \frac{\sum_{i = 1}^{n} RF(p_{i})}{\sum_{i = 1}^{n} RT(p_{i})}$$
 
@@
 
-TODO(eriq): Table
+\begin{table}[H]
+\centering
+\begin{tabular} { l | c | r }
+\hline\hline
+        {\bf $\sum_{i = 1}^{n} RF(p_{i})$} & {\bf $\sum_{i = 1}^{n} RT(p_{i})$} & {\bf Accuracy} \\[0.5ex]
+\hline
+        ? & ? & ? \\[0.5ex]
+\end{tabular}
+\caption{Results}
+\label{tab:results}
+\end{table}
 

### 2012-12-08 paper/paper.tex
Committing minor changes

--- 2012-12-07 paper/paper.tex
@@
 \begin{figure*}[ht]
-   \includegraphics[width=\textwidth px]{images/arch.eps}
+   \includegraphics[width=\textwidth]{images/arch.eps}
         \caption{The Citeopotamus architecture overlaid on a hippopotamus.}
@@
 
-\subsubsection{Structure of Paper Text}
-%TODO(aldrin): Expand here if necessary
-If the paper text was generated from OCR, then the structure of the text was left up to the OCR engine.
-However, papers scraped from PLOS were in HTML and extra formatting can be inferred.
+\subsubsection{Structure of Paper Text}\label{sec:text_structure}
+If the paper text was generated from OCR, then the structure of the text was
+left up to the OCR engine.  However, papers scraped from PLOS were in HTML and
+extra formatting can be inferred.
 
-All text inside top-level $p$ tags can be inferred to be an entire paragraph and was placed on a single line.
-The references section was separated from the rest of the paper by a single line with only ``REFERENCES'' on it.
+All text inside top-level $p$ tags can be inferred to be an entire paragraph
+and was placed on a single line.  The references section was separated from the
+rest of the paper by a single line with only ``REFERENCES'' on it.
 
-\subsection{Structured Paper Directory Format}\label{sec:paperFormat}
-The output of the scraper is a directory that contains information about the root paper and all the reference that were collected.
-To make all the information easily accessible to anyone without imposing any arbitrary restrictions, the structure of the
-data is enforced by directory structure.
+\subsection{Structured Paper Directory Format}\label{sec:dir_structure}
+The output of the scraper is a directory that contains information about the
+root paper and all the reference that were collected.  To make all the
+information easily accessible to anyone without imposing any arbitrary
+restrictions, the structure of the data is enforced by directory structure.
 
-The root directory is named using the root paper's title. Inside the root directory is a ``references'' directory.
-Inside the ``references'' directory are sub-directories named with the number of that citation. A missing directory
+The root directory is named using the root paper's title. Inside the root
+directory is a ``references'' directory.  Inside the ``references'' directory
+are sub-directories named with the number of that citation. A missing directory
 means that the scraper could not collect that reference's information.
@@
 Every directory that represents a paper will have at most four files:
-\begin{enumerate}
-   \item meta.txt -- Contains the title, authors, tags, categories, and abstract. This is the only file required for every paper directory.
-   \item paper.pdf -- The pdf version of the paper.
-   \item paper.txt -- The text version of the paper. This file is required for the root paper.
-   \item refs.txt -- Only the references that appear at the bottom of the paper. This information is duplicated in paper.txt, but placed here for convenience.
-\end{enumerate}
+\begin{description}
+   \item[meta.txt\footnotemark{1}] Contains the title, authors, tags, categories, and abstract.
+                   This is the only file required for every paper directory.
+   \item[paper.txt\footnotemark{1}] The text version of the paper. This file is required for
+                    the root paper.
+   \item[refs.txt\footnotemark{1}] Only the references that appear at the bottom of the paper.
+                   This information is duplicated in paper.txt, but placed here
+                   for convenience.
+   \item[paper.pdf] The pdf version of the paper.
+   \item[paper.html] The HTML version of the paper. This is grabbed should
+                     the paper need to be re-parsed.
+\end{description}
+
+\footnotetext[1]{These files are not required for our implementation to work}
 
@@
 \begin{figure}[ht]
-   \includegraphics[width=\columnwidth px]{images/tree.eps}
+   \includegraphics[width=\columnwidth]{images/tree.eps}
         \caption{The structure of a paper directory.}
@@
 \begin{quote}
-In previous work, the Guyton models were modularized and re-implemented in Fortran, C++ (M2SL \textbf{[]}), and Simulink \textbf{[]}.
+In previous work, the Guyton models were modularized and reimplemented in Fortran, C++ (M2SL \textbf{[]}), and Simulink \textbf{[]}.
 \end{quote}
@@
 \subsubsection{Parsing and Scraping}
-Parsing is vital to the Citeopotamus system. If a context is improperly parsed, then everything else around that citation falls apart.
+Parsing is essential to the Citeopotamus system. If a context is improperly parsed, then everything else around that citation falls apart.
 A spot check of papers that perform poorly (under 10\% accuracy) reveals that many of these these papers have many incorrectly parsed contexts.

### 2012-12-08 paper/paper.tex
I believe this wraps up the background and scraper sections

@@
 \section{Dataset}\label{sec:dataset}
-%TODO(aldrin)
 %overview
@@
 \subsection{Scraper}
-TODO(aldrin)
+The scraper, written in python, extensively uses urllib2 and lxml.html. The
+first task is to access a search landing page using urllib2. Each search result
+page maintains 10 publications per page and links at the top
+and bottom of the search page that lead to other search result pages. Each
+publication located on a search result page is used as a root paper.
+Each listing on the search result page contains metadata for the publication
+listed such as title, author, and path to the HTML of the publication.
+Since we are collecting this dataset programmatically, the HTML
+version is easier to work with than a PDF version of the publication, which
+would require OCR to extract text. Due to the structure of the page (which is
+amazingly consistent), the HTML is parsed in the following sections:
+\begin{itemize}
+   \item Abstract
+   \item Body sections and titles
+   \item References
+      \begin{itemize}
+         \item Search pages for each references paper
+         \item Pubmed page for each reference paper
+         \item Abstract, Title, and Author for refererence paper from pubmed
+      \end{itemize}
+\end{itemize}
+
+First, we extract the abstract text. This is made trivial with lxml's html
+parser, specifically the cssselect and text\_content methods. Similarly, the
+extraction of body section text and titles of publication is easily done.
+Reference papers are more difficult to obtain due to the extra content that
+must be fetched online. Each reference paper listing may or may not have a link
+to a landing page listing various other sources where the publication may be
+found. In cases where there is no link, then this listing is skipped and the
+next one parsed. For cases where there is indeed a link, the pubmed source is
+always picked and the provided pubmed URL to the publication is used to
+retrieve the abstract, title, and authors for the reference paper. While pubmed
+makes extraction of the abstract text somewhat difficult, it is solved through
+the use of text\_content in python's lxml library, which grabs all text from
+child nodes and removes HTML markup. As the necessary information for each
+reference paper is retrieved, the reference paper is written out in the
+appropriate directory location as mentioned below in section
+\ref{sec:dir_structure}.
 
@@
 All text inside top-level $p$ tags can be inferred to be an entire paragraph
-and was placed on a single line.  The references section was separated from the
+which was placed on a single line. The references section was separated from the
 rest of the paper by a single line with only ``REFERENCES'' on it.
+Additionally, the top of the text file listed ``TITLE:'', ``AUTHORS:'', and
+extra information if accessible (which was not the case for PLoS Computational
+Biology, specifically ``TERMS:'' and ``CATEGORIES:'').
 
@@
 The output of the scraper is a directory that contains information about the
-root paper and all the reference that were collected.  To make all the
+root paper and all collected reference papers. To make all the
 information easily accessible to anyone without imposing any arbitrary
@@
 The root directory is named using the root paper's title. Inside the root
-directory is a ``references'' directory.  Inside the ``references'' directory
-are sub-directories named with the number of that citation. A missing directory
+directory is a ``references'' directory and four or five files, described
+below. Inside the ``references'' directory are sub-directories for each
+citation number in the root paper. The information for reference papers are
+maintained in the appropriately numbered directory, such that a reference paper
+``foo'', is the fourth citation (i.e. appears in the root paper as ``[4]'')
+then information for paper ``foo'' is maintained in the directory ``4'' in the
+root paper's ``references'' directory. A missing directory
 means that the scraper could not collect that reference's information.
@@
 Every directory that represents a paper will have at most four files:
-\begin{description}
-   \item[meta.txt\footnotemark{1}] Contains the title, authors, tags, categories, and abstract.
-                   This is the only file required for every paper directory.
-   \item[paper.txt\footnotemark{1}] The text version of the paper. This file is required for
-                    the root paper.
-   \item[refs.txt\footnotemark{1}] Only the references that appear at the bottom of the paper.
-                   This information is duplicated in paper.txt, but placed here
+\begin{itemize}
+   \item \textbf{meta.txt}\footnotemark[1]{} -- Contains the title, authors,
+                                                tags, categories, and abstract.
+                                                This is the only file required
+                                                for every paper directory.
+   \item \textbf{paper.txt}\footnotemark[1]{} -- The text version of the paper.
+                                                 This file is required for the
+                                                 root paper.
+   \item \textbf{refs.txt}\footnotemark[1]{} -- Only the references that appear
+                                                at the bottom of the paper.
+                                                This information is duplicated
+                                                in paper.txt, but placed here
                                                 for convenience.
-   \item[paper.pdf] The pdf version of the paper.
-   \item[paper.html] The HTML version of the paper. This is grabbed should
-                     the paper need to be re-parsed.
-\end{description}
+   \item \textbf{paper.pdf} -- The pdf version of the paper.
+   \item \textbf{paper.html} -- The HTML version of the publication. This is
+                                grabbed should the paper need to be re-parsed.
+\end{itemize}
 
-\footnotetext[1]{These files are not required for our implementation to work}
+\footnotetext[1]{These files \textbf{are required} for our implementation to work}
 

### 2012-12-08 paper/paper.tex
Paper should be donezo

@@
 
-The rest of the paper is laid out as follows. Section \ref{sec:contributions}
-is about what we are contributing. The following section describes out testing
-dataset. We then talk about our architecture we created to solve the problem.
-Then we go into how we parse papers and discuss the methods for choosing the
-best citation. Then we go into future work, related work, and lastly our
-conclusion.
-
-\section{Contributions}\label{sec:contributions}
-Our contributions consist of a dataset to test new solutions and methods to
-recommend citations given a location for a citation.
+This paper discusses our approach to this problem, as well as the dataset we
+procured for this use. In section \ref{sec:dataset} we highlight our dataset,
+where it came from and what it contains. Section \ref{sec:architecture} follows
+up with how we designed the system, our method of collecting our dataset, and
+how it is structured, while section \ref{sec:parsing} goes into detail of how
+our system parses and understands the publication text. Section
+\ref{sec:methods} describes our methods for predicting a citation and section
+\ref{sec:eval} discusses our approach for evaluating our system. Our results
+are shown in section \ref{sec:results}, section \ref{sec:future} is where we
+talk about future work and we discuss related work in section
+\ref{sec:related}. Finally, we conclude our work in section
+\ref{sec:conclusion}.
 
@@
 
-\subsection{Scraper}
+\subsection{Scraper}\label{sec:scrape}
 The scraper, written in python, extensively uses urllib2 and lxml.html. The
@@
 
-\section{Evaluation}
+\section{Evaluation}\label{sec:eval}
 To evaluate our system, we find the total number of references that we have successfully placed.

### 2012-12-08 code/citer/citer.py
Ignoring incorrect citations

@@ -7,7 +7,8 @@ from constants import DEBUG
 import method
 import parser
 
-DATA_DIR = '../data'
+#DATA_DIR = '../data'
+DATA_DIR = '/home/eriq/aldrin/data'
 
 AVAILABLE_METHODS = [
                      method.PreContextTitleAuthorMethod,
@@ -32,6 +33,11 @@ def main():
    if '-p' in sys.argv:
       paperName = sys.argv[sys.argv.index('-p') + 1]
    paper = parser.parseFullDataset(paperName)
+
+   if not paper:
+      print "Error parsing paper"
+      return
+
    print paper
 
    # Ordering mode
@@ -45,20 +51,38 @@ def fullTest():
    allHitRefs = set()
    allRefs = set()
 
+   #TEST
+   totalCount = 0
+   keep = []
+
    for paperName in os.listdir(DATA_DIR):
       paper = None
 
       try:
+         #TEST
+         totalCount += 1
+
          paper = parser.parseFullDataset(DATA_DIR + '/' + paperName)
+         if not paper:
+            print "Error parsing " + paperName
+            continue
+
+         #TEST
+         keep.append(paperName)
+
          paperRes = normalRun(paper)
+         if paperRes:
+            allHitRefs.update(paperRes[2])
+            allRefs.update([ ref.title.strip().upper() for ref in paper.references.values()])
 
-         allHitRefs.update(paperRes[2])
-         allRefs.update([ ref.title.strip().upper() for ref in paper.references.values()])
-
-         res.append((paperRes[0], paperRes[1]))
+            res.append((paperRes[0], paperRes[1]))
       except OSError:
          print "Error parsing paper: " + paperName
          continue
+
+   #TEST
+   print "\n\n------------------------\n\n"
+   print "{} / {}".format(len(keep), totalCount)
 
    res = sorted(res, reverse = True)
    total = 0
@@ -108,6 +132,9 @@ def normalRun(paper):
             else:
                misses += 1
             break
+
+   if total == 0:
+      return None
 
    return ((float(hits) / total),
            "{:.2%}\t(Hits: {},\tMisses: {},\tTotal: {})\t{}".format((float(hits) / total), hits, misses, total, paper.title),

### 2012-12-08 code/citer/parser.py

@@ -63,13 +63,15 @@ def parseDir(dirName):
 # 'citationKey' will be an array of citations in the order that they appear in the text.
 # Both 'noNumbersText' and 'noCitationsText' will not contain anything in or after after the references section.
 # NOTE: This will probably not be effective if it is not one paragraph per line.
-def parseCitations(entry):
+def parseCitations(entry, references):
    noNumbersText = ''
    noCitationsText = ''
    citations = []
    citationKey = []
    # For when we see the references
    noMoreCitations = False
+
+   referenceCount = 0
 
    parsedText = entry['fullText']
 
@@ -102,6 +104,39 @@ def parseCitations(entry):
 
       if re.search('REFERENCES', rawLine):
          noMoreCitations = True
+         currentReference = 0
+         continue
+
+      if noMoreCitations:
+         # In references.
+         currentReference += 1
+
+         match = re.match('\[\s*(\d+)\s*\]\s*(.*)', rawLine)
+         if not match:
+            print "ERROR: could not parse reference"
+            return None
+
+         if int(match.group(1)) != currentReference:
+            print "ERROR: reference does not match position"
+            return None
+
+         if not references.has_key(int(match.group(1))):
+            continue
+
+         # Verify that all the authors are present.
+         reference = match.group(2).upper().strip()
+         authors = [ author.upper().strip() for author in re.findall('\w{3,}', ' '.join(references[currentReference]['meta']['authors'])) ]
+
+         # Remove incorrect references
+         for author in authors:
+            if not author in reference:
+               #print "ERROR: Author not found in reference: {}, ({})".format(author, reference)
+               #TEST
+               #return None
+               references.pop(currentReference)
+               break
+
+         referenceCount += 1
 
       if not noMoreCitations and re.search('\[\s*\d+\s*\]', rawLine):
          cites = re.findall('\[\s*\d+\s*\]', rawLine)
@@ -170,6 +205,16 @@ def parseCitations(entry):
    entry['citationKey'] = citationKey
    entry['citations'] = citations
 
+   if len(references) == 0:
+      print "ERROR: Paper does not have any references"
+      return None
+
+   return True
+   #TEST
+   #if referenceCount != 0:
+   #   print referenceCount
+   #return referenceCount == 0
+
 
 # Parse an entire directory structure.
 # At the root should be the base paper, and then references/ should contain all the reference papers.
[…]

### 2012-12-08 paper/paper.tex
Added a note about the unfortunate state of our data in the directory structure sub section of Architecture

@@
 means that the scraper could not collect that reference's information.
+
+Unfortunately, there was a problem as we were writing the information for some
+of these reference papers to disk. In some cases the directory containing information for a
+reference paper is incorrectly labelled. Specifically, as with the example
+above, if we have a reference paper ``foo'' that is the fourth citation, our
+dataset, as is, may have ``foo'' in a directory ``5.'' That is, instead of
+``[4]'' being in the directory ``4,'' it is in the directory ``5.'' While this
+is unfortunate, and can be redone (the raw HTML for every root paper has
+information that would allow the reference directories to be properly renamed),
+it could not be fixed at the time of getting results. So the results mentioned
+in this paper reflect appropriate measures taken during the parsing phase,
+further described in section \ref{sec:parsing}.
 

### 2012-12-08 paper/paper.tex
results and some paper

--- 2012-12-08 paper/paper.tex
@@
 
+\subsection{Incorrect References}
+Sometimes their is an error in scraping which causes a reference to take on the incorrect number.
+To prevent these refernces from polluting our data, we check for them at during parsing.
+We parse the refernce section of the paper and look at every reference. If the reference does not contain all of the author names with
+more than three letters, then we drop the reference and assume it is incorrect.
+If there are no references left after all the references have been parsed, then the entire paper is droped.
+Of our original 102O papers, 720 made it pass this phase.
+
 \section{Methods}\label{sec:methods}
@@
 \centering
-\begin{tabular} { l | c | r }
+\begin{tabular} { l | c | c | r }
 \hline\hline
-        {\bf $\sum_{i = 1}^{n} RF(p_{i})$} & {\bf $\sum_{i = 1}^{n} RT(p_{i})$} & {\bf Accuracy} \\[0.5ex]
+        {\bf Reference Material} & {\bf $\sum_{i = 1}^{n} RF(p_{i})$} & {\bf $\sum_{i = 1}^{n} RT(p_{i})$} & {\bf Accuracy} \\[0.5ex]
 \hline
-        ? & ? & ? \\[0.5ex]
+        Abstract and Reference & 3146 & 11840 & 0.2657 \\[0.5ex]
+\hline
+        Abstract Only & 2642 & 11840 & 0.2231 \\[0.5ex]
+\hline
+        Reference Only & 1576 & 11840 & 0.1331 \\[0.5ex]
 \end{tabular}
@@
 We have found that automatic citation placement is a difficult, but doable problem.
+Even with only the information that appears on the page, we were able to achieve over 10\% accuracy.
 

### 2012-12-08 code/citer/citer.py

@@ -11,8 +11,8 @@ import parser
 DATA_DIR = '/home/eriq/aldrin/data'
 
 AVAILABLE_METHODS = [
-                     method.PreContextTitleAuthorMethod,
-                     method.SentenceTitleAuthorMethod,
+                     #method.PreContextTitleAuthorMethod,
+                     #method.SentenceTitleAuthorMethod,
                      method.PreContextAbstractWordsMethod,
                      method.SentenceContextAbstractBigramsMethod,
                      method.PreContextAbstractBigramsMethod,

### 2012-12-08 paper/paper.tex
Fixed some spelling.

--- 2012-12-08 paper/paper.tex
@@
 cite6, cite7, cite8}. Solutions range from graph based social network
-approaches to language models to match meaning in both the paper and the
-recommended text. But the problem of recommending where inside the paper to put
+approaches to language models that match meaning in both the paper and the
+recommended text. On the other hand the problem of recommending where inside the paper to put
 citations is unknown. The ideal solution would recommend an exact spot in the
@@
 This paper discusses our approach to this problem, as well as the dataset we
-procured for this use. In section \ref{sec:dataset} we highlight our dataset,
+procured for testing and future work on this problem..
+In section \ref{sec:dataset} we highlight our dataset,
 where it came from and what it contains. Section \ref{sec:architecture} follows
@@
 
-Unfortunately, there was a problem as we were writing the information for some
-of these reference papers to disk. In some cases the directory containing information for a
-reference paper is incorrectly labelled. Specifically, as with the example
-above, if we have a reference paper ``foo'' that is the fourth citation, our
-dataset, as is, may have ``foo'' in a directory ``5.'' That is, instead of
-``[4]'' being in the directory ``4,'' it is in the directory ``5.'' While this
-is unfortunate, and can be redone (the raw HTML for every root paper has
-information that would allow the reference directories to be properly renamed),
-it could not be fixed at the time of getting results. So the results mentioned
-in this paper reflect appropriate measures taken during the parsing phase,
-further described in section \ref{sec:parsing}.
-
-Every directory that represents a paper will have at most four files:
+Every directory that represents a paper will have at most five files:
 \begin{itemize}
@@
 The citer begins by attempting to parse a directory structure into a structured collection of papers.
-The citer then pre-processed each paper and generates a set of contexts (see Section \ref{sec:context}) for each citation in each
+The citer then pre-processes each paper and generates a set of contexts (see Section \ref{sec:context}) for each citation in each
 root paper.
@@
 that operate on the contexts to try and generate citations. Each citation in put through each method one at a time. If any method emits a value, then the pipeline
-it short circuited and the emitted value is used as the citation. Because of this short circuiting behavior, the methods in the pipeline are ordered by approximate
+is short circuited and the emitted value is used as the citation. Because of this short circuiting behavior, the methods in the pipeline are ordered by approximate
 precision. That is, all of the methods that rarely miss (regardless of how many citations they correctly place) are moved to the front of the pipeline.
@@
 \subsection{OCR}
-Before any parsing can be done a paper, it must first be converted to a plain text (UTF-8) format.
+Before any parsing can be done on a paper, it must first be converted to a plain text (UTF-8) format.
 Since PLOS provides most of their papers in an HTML format, this only had to be done off-line for a few
@@
 This is especially seen when an author is referencing background material. These ranges must be expanded out to
-the fill list of citations: $$[1][2][3]$$
+the full list of citations: $$[1][2][3]$$
 
@@
 citations. To combat the punctuation tokenizing problem, we decided to only split sentence on periods, question marks, and
-exclamations points. Additionally, we replaced common false positive sentence enters i.e.
+exclamations points. Additionally, we replaced common false positive sentence enders i.e.
 $$i.e. => \_ie\_$$
@@
 \subsubsection{Sentence}
-Sentence level contexts contain just the sentence that the citation was main in. As discussed in Section \ref{sec:fpEnders},
+Sentence level contexts contain just the sentence that the citation was made in. As discussed in Section \ref{sec:fpEnders},
 sentence context is parsed just by splitting the paragraph on sentence ending punctuation after false positives have been replaced.
@@
 
-Using synonym can also help finding important words.
+Using synonyms could also help finding important words.
 
@@
 We were unable to find any related work on recommending citations given a spot for a citation to go.
-Unlike the problem of recommending citations for a paper.
-Copious amounts of work already exists on the topic.
-With several different approaches.
-One of the most common was using models to compare a paper and the rest of the dataset.
-Some of the models used includes translation models, probabilistic models, and several forms of LDAs.\cite{cite1, cite2, cite3} The next most common group of solutions was to use citations graphs to recommend missing citations.\cite{cite6} One group extended the notion of graphs and included metadata to help filter out results.\cite{cite4} One of the most
+Unlike the problem of recommending citations for a paper. Copious amounts of work already exists on the topic.
+With several different approaches. One of the most common was using models to compare a paper and the rest
+of the dataset. Some of the models used included translation models, probabilistic models, and several
+forms of LDAs.\cite{cite1, cite2, cite3} The next most common group of solutions was to use citations
+graphs to recommend missing citations.\cite{cite6} One group extended the notion of graphs and included metadata to help filter out results.\cite{cite4} One of the most 
 interesting and unique approaches was to not look at co-citations but to look at co-accesses via logs like HTTP access records.\cite{cite7}
 Another interesting approach used collaborative filtering to let communities help decide citations.\cite{cite8} For more related work in
-citation recommendation we recommend the survey by McNee et al. they go into a lot of depth on the problem and common pitfalls.\cite{cite5}
+citation recommendation we recommend the survey by McNee et al. because they go into a lot of depth on the problem and common pitfalls.\cite{cite5}
 
@@
 \section{Thanks}
-We thanks the folks at PLOS for providing the source of our dataset. Without them this would of been a lot harder.
+We thank the folks at PLOS for providing the source of our dataset. Without them this would of been a lot harder.
 

### 2012-12-08 paper/paper.tex

@@
 
+Unfortunately, there was a problem as we were writing the information for some
+of these reference papers to disk. In some cases the directory containing information for a
+reference paper is incorrectly labelled. Specifically, as with the example
+above, if we have a reference paper ``foo'' that is the fourth citation, our
+dataset, as is, may have ``foo'' in a directory ``5.'' That is, instead of
+``[4]'' being in the directory ``4,'' it is in the directory ``5.'' While this
+is unfortunate, and can be redone (the raw HTML for every root paper has
+information that would allow the reference directories to be properly renamed),
+it could not be fixed at the time of getting results. So the results mentioned
+in this paper reflect appropriate measures taken during the parsing phase,
+further described in section \ref{sec:parsing}.
+
 Every directory that represents a paper will have at most five files:
@@
 
+\subsection{Incorrect References}
+Sometimes there is an error in scraping which causes a reference to take on the incorrect number.
+To prevent these refernces from polluting our data, we check for them during parsing.
+We parse the refernce section of the paper and look at every reference. If the reference does not contain all of the author names with
+more than three letters, then we drop the reference and assume it is incorrect.
+If there are no references left after all the references have been parsed, then the entire paper is droped.
+Of our original 102O papers, 720 made it passed this phase.
+
 \section{Methods}\label{sec:methods}
